### 2014-03-09 proposal.tex
Completed intro and problem. Just need to write the proposal itself and review.

\documentclass[10pt,a4paper]{article}

\usepackage{fullpage}

\title{Proposal to explore the feasibility of improving BBC Search through the use of Linked Data}
\author{Ross Fenning}

\begin{document}

\maketitle
\thispagestyle{empty}

\section{Introduction}

BBC Search is a online product that forms part of the BBC's online presence so
that users can search for and navigate all areas of the BBC website using
free text queries. This might aid visitors who are unable to find their desired
content via other global or site-specific navigation or those who are simply
looking for things that fall below the radar of the latest, greatest or
otherwise promoted content.

General-purpose search engines such as Google are also capable of directing
users to BBC pages via free text queries, but there is a benefit the BBC
can bring with its own search service that has greater knowlege of the
BBC's own content. The BBC can use internal knowledge to predict a user's
intent (if the query matches a programme title, then show links to watch
the latest episode on iPlayer) or to provide editorially-curated
links to significant pages (e.g. if a user searches for a term
related to a major, ongoing news theme, curated links can always
link to an overview or FAQ for that ongoing event for those
looking for the background on it).

\section{The Problem}

The BBC Search service relies on a backend search engine to provide
full-text querying, which provides pages of results in a manner not
too dissimilar to Google. Internal BBC knowledge allows the results
to be broken up into logical ``zones'', but those full-text results
(sometimes referred to as the \emph{Organic Results} are matched
on little more than traditional Information Retrieval ranking
algorithms and linguistic techniques.

The search pages are therefore augmented with features such as
``Editor's Choice'' where text matching is done against a separate
system to provide manually-curated ``best links'' for a given
concept. This provides a useful bridge to recommended pages based
on precise concepts the user might be seeking and gives the system
the appearance of understanding that the user was seeking a
particular concept rather than just pages that happen to contain
the same text.

For example, a search for ``manchester'' gives
us an Editor's Choice link for the index page for Manchester local
news within BBC News. This is a top link above any matches for pages
that happen to mention Manchester.

This is a good feature which could be compared to Google's
``Knowledge Graph'', but falls short due to the need for all links
to be curated by hand against a manually-constructed taxonomy of terms.

The Editor's Choice feature is also limited only to matching a
concept title to a recommended page link. There is no semantic
representation of the given concept that might allow richer linking
to multiple pages. For example, a search for an actor's name might
provide a recommended profile page within an Editor's Choice system,
but a deeper understanding of the person they are searching for might
allow automatic aggregation of recent news mentioning that actor and
all BBC programmes past and future in which they appear. Recommended
and curated links could still form part of these links, but there
is much that could be done with automatically linking entities and pages.

\section{Proposal}

\end{document}

### 2014-03-17 proposal.tex
Added a bit to the actual proposal section and reworded some earlier bits.

@@
 
-\usepackage{fullpage}
+%\usepackage{fullpage}
 
@@
 links to significant pages (e.g. if a user searches for a term
-related to a major, ongoing news theme, curated links can always
+related to a major, ongoing news theme, curated links can
 link to an overview or FAQ for that ongoing event for those
@@
 
-The BBC Search service relies on a backend search engine to provide
+The BBC Search service relies on an underlying search engine to support
 full-text querying, which provides pages of results in a manner not
@@
 (sometimes referred to as the \emph{Organic Results} are matched
-on little more than traditional Information Retrieval ranking
+just using traditional Information Retrieval ranking
 algorithms and linguistic techniques.
@@
 ``Editor's Choice'' where text matching is done against a separate
-system to provide manually-curated ``best links'' for a given
-concept. This provides a useful bridge to recommended pages based
+system to provide manually-curated ``best links'' for a particular
+search terms. This provides a useful bridge to recommended pages based
 on precise concepts the user might be seeking and gives the system
-the appearance of understanding that the user was seeking a
-particular concept rather than just pages that happen to contain
+the appearance of understanding that the user was seeking those
+particular concepts rather than just pages that happen to contain
 the same text.
@@
 
-This is a good feature which could be compared to Google's
-``Knowledge Graph'', but falls short due to the need for all links
+This is a useful feature which could be compared to Google's
+`Knowledge Graph'', but falls short due to the need for all links
 to be curated by hand against a manually-constructed taxonomy of terms.
@@
 The Editor's Choice feature is also limited only to matching a
-concept title to a recommended page link. There is no semantic
+concept by title to a recommended page link. There is no semantic
 representation of the given concept that might allow richer linking
@@
 
+The proposal is to conduct an analysis and feasibility study of how
+the Search product could benefit from \emph{Linked Data} and how
+it has been applied in other parts of the BBC and perhaps globally.
+
+The analysis will look not only at what linked and semantic data is already
+present in different pieces of content across the BBC that Search is
+indexing, but also might provide proposals for how greater adoption
+of Linked Data concepts might enable Search to provide better discovery
+of that content.
+
+The provision of better results might be achieved through use of additional
+metadata linked to content items or the search results page might
+at least be able to decorate relevant -- as determined by the
+full-text search engine -- results with richer onward links, visual iconography
+or calls to action.
+
+The study may be able to provide automated replacements for
+manually-maintained systems such as ``Editor's Choice'' or manual
+tagging of content. Known synonyms for concepts that have to be fed into
+the Search application from Editorial teams could be sourced automatically.
+Where manual curation and review of content must take place, automated
+tools might be able to assist and suggest information, which would
+speed up such manual workflows.
+
 \end{document}

### 2014-03-19 proposal.tex
First draft of proposal complete.

@@
 
-BBC Search is a online product that forms part of the BBC's online presence so
-that users can search for and navigate all areas of the BBC website using
+BBC Search is an online product that forms part of the BBC website
+to enable users to search for and navigate all areas of the site using
 free text queries. This might aid visitors who are unable to find their desired
@@
 BBC's own content. The BBC can use internal knowledge to predict a user's
-intent (if the query matches a programme title, then show links to watch
+intent (e.g. if the query matches a programme title, then show links to watch
 the latest episode on iPlayer) or to provide editorially-curated
@@
 too dissimilar to Google. Internal BBC knowledge allows the results
-to be broken up into logical ``zones'', but those full-text results
-(sometimes referred to as the \emph{Organic Results} are matched
+to be broken up into logical ``zones'' (News, iPlayer, Sport, etc.),
+but those full-text results
+-- sometimes referred to as the \emph{Organic Results} -- are matched
 just using traditional Information Retrieval ranking
@@
 The search pages are therefore augmented with features such as
-``Editor's Choice'' where text matching is done against a separate
+\emph{Editor's Choice} where text matching is done against a separate
 system to provide manually-curated ``best links'' for a particular
-search terms. This provides a useful bridge to recommended pages based
+search term. This provides a useful bridge to recommended pages based
 on precise concepts the user might be seeking and gives the system
@@
 This is a useful feature which could be compared to Google's
-`Knowledge Graph'', but falls short due to the need for all links
+\emph{Knowledge Graph}, but is somewhat limited due to the need for all links
 to be curated by hand against a manually-constructed taxonomy of terms.
@@
 The Editor's Choice feature is also limited only to matching a
-concept by title to a recommended page link. There is no semantic
+concept by title to recommended pages. There is no semantic
 representation of the given concept that might allow richer linking
-to multiple pages. For example, a search for an actor's name might
+to related pages. For example, a search for an actor's name might
 provide a recommended profile page within an Editor's Choice system,
@@
 
-The provision of better results might be achieved through use of additional
+The provision of better results might be achieved through indexing additional
 metadata linked to content items or the search results page might
-at least be able to decorate relevant -- as determined by the
-full-text search engine -- results with richer onward links, visual iconography
-or calls to action.
+at least be able to decorate relevant results with richer onward links,
+visual iconography or calls to action. Logic, inference and OWL may also provide
+alternative search methodologies that replace or complement text-based
+algorithms and retrieval techniques.
 
-The study may be able to provide automated replacements for
+The study may be able to suggest automated replacements for
 manually-maintained systems such as ``Editor's Choice'' or manual
@@
 
+Another focus of the analysis will be how Linked Data approaches
+could feed into the Search application's own modelling and indexing
+of other products' content. A search application that models not
+just the textual content of pages, but also linked concepts and
+entities might be able to serve a broader range of queries
+such as requests for automatic aggregation of new content around
+a concept or perhaps some natural language queries.
+
+By taking BBC Search beyond the traditional approaches of indexing
+documents and text-based retrieval, it may be feasible to propose
+evolving the product into a wider ``content discovery'' system
+that aggregates enough metadata around all BBC content to provide
+a multitude of use cases for browsing, discovering and otherwise
+reasoning amongst those content items.
+
 \end{document}

### 2014-03-20 proposal.tex
Added a hyphen.

@@
 to enable users to search for and navigate all areas of the site using
-free text queries. This might aid visitors who are unable to find their desired
+free-text queries. This might aid visitors who are unable to find their desired
 content via other global or site-specific navigation or those who are simply

### 2014-04-14 paper.tex
Made some headway with the background.

\documentclass[10pt,a4paper]{report}

\title{}
\author{Ross Fenning}

\begin{document}

\maketitle

\chapter{Background}

This report proposes improvements to the BBC Search product making use
of \emph{Linked Data} \cite{} and/or the Semantic Web \cite{}. I hope
to be able to demonstrate five tangible benefits this domain can
bring to a search application, namely:

\begin{enumerate}
  \item Further decoupling of BBC applications, which aids scalability,
    maintainability and resilience in many software architectures. \cite{}
  \item Improvements to the search results page that help users determine
    if the results given are relevant via so-called \emph{Rich Snippets}
    that can automatically display some semantic information about a given
    result without the need for manual curation.
  \item User experience and design improvements to the search results
    where semantic properties about the results can drive visual sugar
    and calls to action, which can allow for a more flexible and
    adaptable design without the need to enumerate all ``kinds'' with
    different templates.
  \item Removal of the manual curation of the ``Editor's Choice'' results
    against a given query and replacing it with curated linked data that
    can provide recommended content against queries in a more general
    manner.
  \item Replacement of the manual curation of autocomplete suggestions
    in the \emph{Search Suggest} service -- that suggests full text queries
    as the user types -- with suggestions driven from linked data.
\end{enumerate}

In the rest of this chapter, I will give an overview of what role BBC
Search plays and how we can usefully view the system as a whole as four
distinct subsystems. In later chapters we can then look to improve these
four separate systems one at a time and then evaluate how these improvements
might complement each other.

\section{BBC Search}

BBC Search is an online product that forms part of the BBC website
to enable users to search for and navigate all areas of the site using
free-text queries. This might aid visitors who are unable to find their desired
content via other global or site-specific navigation or those who are simply
looking for things that fall below the radar of the latest, greatest or
otherwise promoted content.

General-purpose search engines such as Google are also capable of directing
users to BBC pages via free text queries, but there is a benefit the BBC
can bring with its own search service that has greater knowlege of the
BBC's own content. The BBC can use internal knowledge to predict a user's
intent (e.g. if the query matches a programme title, then show links to watch
the latest episode on iPlayer) or to provide editorially-curated
links to significant pages (e.g. if a user searches for a term
related to a major, ongoing news theme, curated links can
link to an overview or FAQ for that ongoing event for those
looking for the background on it).

It is well established that a classical information retrieval system
can be expressed as two sets of computation: processing of information
into indexes (also known as \emph{indexing}) for quicker retrieval
and the retrieval of documents from those indexes based on a user's
query. These can be known as \emph{index time} or \emph{query time}
processing respectively.

The general strategy is to perform
any expensive transformation, expansion or ordering of the indexed
at index time so that query time algorithms may be optimised to
run as quickly as possible. This is an approach that has only
increased in importance as information retrieval systems have moved
from standalone systems (e.g. a catalogue search situated within
a library used by a handful of users at once) to web-based
searches across a far larger corpus with tens or even hundreds of
users submitting queries in a single second.

In the remaining sections of this chapter, I outline the considerations
around these two sides of the search application in addition to the
two complementary systems known as \emph{Editor's Choice} and
\emph{Search Suggest}.

\section{Indexing Content}

The Search application needs to read in or receive metadata about
BBC content from a variety of sources and then needs to serve
a diverse set of use cases. \cite{fenning2014applicability} The
need to integrate against different data sources and funnel
that information into a common set of search indexes can
typically be seen as an \emph{enterprise integration}
problem. Architectural patterns have been developed, tested and
implemented in a large number of enterprises to synchronise,
transform and normalise data. Such patterns are notably
summarised by Hohpe and Woolf\cite{hohpe2004enterprise}.

In more recent years, a growing trend has emerged to use
\emph{Linked Data} in the enterprise to remove the need
for repeated integration projects or data warehousing.
\cite{allemang2010semantic}

\section{Retrieving Content}

\section{Curation}

\chapter{State of the Art in Linked Data}

\chapter{Analysis}

\chapter{Proposal}

\chapter{Implementation Plan}

\chapter{Summary}

\bibliographystyle{cell}
\bibliography{bibtex}

\end{document}

### 2014-04-16 paper.tex
Made some headway with the introduction.

@@
 
-\title{}
+\title{Proposal to improve BBC Search through the use of Linked Data}
 \author{Ross Fenning}
@@
 
-In more recent years, a growing trend has emerged to use
-\emph{Linked Data} in the enterprise to remove the need
-for repeated integration projects or data warehousing.
-\cite{allemang2010semantic}
+Some of the data is fairly flat, textual content such as articles and some
+information -- such as programmes -- is very structured (e.g. programmes,
+series, episodes, times of broadcast, channel on which they are broadcast,
+what times they are available to watch on iPlayer, what kinds of devices
+are permitted by rights to watch them on iPlayer). This has challenges
+for providing a consistent and meaningful user experience across such
+a heterogenous mix of content.
+
+% Do we need this?
+Concepts central to the information retrieval domain such as creating
+tokenisation, stemming, lemmatisation and relevance
+algorithms can normally be delgated to
+third party proprietary or free software. It is still useful however
+for developers of full search application to be aware of these concepts even
+if their implementation is abstracted away. Tokenisation, stemming and
+lemmatisation are index time concerns, the full definitions of which
+are out of scope for this report. In short, we want a search application
+to understand individual words within an article and to understand that, for
+example, ``mice'' and ``mouse'' are approximately the same word as well
+as verb forms like ``swim'', ``swam'', ``swum'' and ``swimming'' all being
+equivalent in the context of keyword retrieval.
 
@@
 
-\section{Curation}
+\section{Editor's Choice}
+
+\section{Search Suggest}
 
 \chapter{State of the Art in Linked Data}
+
+\section{Linked Enterprise Data}
+
+In recent years, a growing trend has emerged to use
+\emph{Linked Data} in the enterprise to remove the need
+for repeated integration projects or data warehousing.
+\cite{allemang2010semantic} If we view the indexing processes
+of a search application as a variant of data warehousing,
+we can start to argue for enterprise-wide publishing of
+linked data as a more cost effective means of building search
+indexes over bespoke integration efforts.
+
+An important consideration is that BBC Search is largely directing
+users to public pages on the BBC website, a large number of which have
+already published some of their metadata as linked data. Notably, BBC News,
+BBC Sport and BBC Food all use some combination
+of microformats, microdata, RDFa, HTML meta tags within their HTML content
+pages. Some of this was to improve search results in external search engines
+such as Google and some of it ties into Facebook's Open Graph Protocol, which
+enables and enhances social media sharing of the pages.
+
+These efforts are not as structured and rich as the more notable uses
+of semantic web technologies on the programmes microsites, Nature and BBC
+Music \cite{}, but indicate that some level of metadata can be retrieved
+as linked data. In cases where the metadata are rich enough, it might be
+possible to avoid direct integration with databases, hidden back end
+web services and other structured ``feeds'' typically set up for enterprise
+integration.
 

### 2014-04-18 paper.tex
Written up about Editor's Choice.

@@
 This report proposes improvements to the BBC Search product making use
-of \emph{Linked Data} \cite{} and/or the Semantic Web \cite{}. I hope
-to be able to demonstrate five tangible benefits this domain can
-bring to a search application, namely:
+of \emph{Linked Data} \cite{bizer2009linked} and/or the Semantic Web
+\cite{berners2001semantic}. I hope to be able to demonstrate five tangible
+benefits this domain can bring to a search application, namely:
 
@@
 In the rest of this chapter, I will give an overview of what role BBC
-Search plays and how we can usefully view the system as a whole as four
+Search plays and how we can usefully view the system as four
 distinct subsystems. In later chapters we can then look to improve these
@@
 users to BBC pages via free text queries, but there is a benefit the BBC
-can bring with its own search service that has greater knowlege of the
+can bring with its own search service that has greater knowledge of the
 BBC's own content. The BBC can use internal knowledge to predict a user's
@@
 for providing a consistent and meaningful user experience across such
-a heterogenous mix of content.
+a heterogeneous mix of content.
+
+We can achieve some uniformity of the data by building a single, common
+API through which all content is fed into the Search application. However,
+it varies based on practicalities whether
+work is done by the owners of the content to send content to the API
+or whether the developers of the Search application need to integrate
+existing feeds via an adapter pattern. Some pages on the BBC website no
+longer have a dedicated team maintaining them and can sometimes only
+be discovered via a web crawl as an external search engine would do. A lot
+of metadata about content also lives in a diverse range of databases and
+content management systems, which can be collectively described as part
+of the so-called \emph{deep web}. \cite{}
+
+In chapter~\ref{stateoftheart}, we will discuss how the deep web is one
+problem the linked data domain seeks to solve.
 
@@
 tokenisation, stemming, lemmatisation and relevance
-algorithms can normally be delgated to
+algorithms can normally be delegated to
 third party proprietary or free software. It is still useful however
@@
 
+Once we have constructed an index optimised for keyword-based retrieval,
+we can begin to run queries against that index. A retrieval problem
+can be summarised as trying to maximise two separate measures: \emph{precision}
+and \emph{recall}, where:
+
+\begin{equation}
+  precision = \quot{|{relevant documents}\and{retrieved documents}|}{|{retrieved documents}|}
+\end{equation}
+
+\begin{equation}
+  recall = \quot{|{relevant documents}\and{retrieved documents}|}{|{relevant documents}|}
+\end{equation}
+
+Namely, precision is the fraction of the retrieved documents that were
+relevant to the user's query and recall is the fraction of documents out of
+all possible, relevant documents that appear in the search results.
+
+Note that a system could trivially maximise recall by always returning all
+results, but such a system would perform poorly in terms of precision. A
+measure known as \emph{F-measure} was derived by van Rijsbergen \cite{} which
+balances precision recall based on preferring recall over precision \beta
+times:
+
+% TODO: equation
+
+There are other measures such as average precision and average mean precision
+that take into account ordering of results and the average over multiple
+queries respectively. A successful algorithm or third party search engine
+application can be evaluated quantitatively by these measures and more. A more
+qualitatively summary from the perspective of the end users could be:
+
+\begin{quote}
+A successful search application will return only the content the user wants
+(precision) --
+as high up the results list as possible -- and as much of desired content
+as possible (recall).
+\end{quote}
+
+The set of all documents that could be retrieved by a query is known as the
+\emph{corpus} and search systems will typically apply a \emph{score} against
+each that gives some measure of confidence of the relevance of each document
+given a particular query. It should be noted that scores are a relative
+metric only and only have meaning within the context of a particular
+retrieval algorithm and particular query.
+
 \section{Editor's Choice}
+
+The current BBC Search application returns an ordered list of results
+for queries based on keyword matching within the titles, text or other
+chosen metadata fields as appropriate. However, there are cases where
+the algorithms employed may not return something noted as the official
+or canonical match for a concept, person, programme, etc. (e.g. the
+official microsite for a popular BBC programme or a profile page for
+a notable person on BBC News).
+
+Editorial staff thus have control over a curation system that manifests
+as an \emph{Editor's Choice} feature that will ensure the top one to three
+results for popular queries link to manually-chosen pages deemed as the most
+relevant pages for those queries. For instance, a search for a city such
+as Coventry might naturally return recent news articles that mention the
+city (since news results are biased towards more recent articles over older
+ones), but the Editor's Choice links on top of the so-called \emph{organic
+results} can persistently offer users links for common use cases such as
+the BBC Weather page for Coventry.
+
+Each and every link promoted within this feature is hand-chosen by editorial
+staff and much manual effort is needed to keep promoting new concepts
+as they appear and to remove pages as they get superseded. It is hoped
+in this proposal we can reduce some of that manual curation through the use
+of linked data and demonstrate ways editorial staff can focus on curating
+their own linked data such that Editor's Choice could evolve into a more
+generalised and automated subsystem. A metadata-driven curation system
+could use common patterns in the data to promote orders of magnitude more
+top links with a fraction of the current effort.
 
@@
 
+One challenge for the querying of a search application is to be tolerant
+of variable quality of user-entered queries. Many users of web search
+engines may give ambiguously short queries, overly long queries with (where
+it can be hard for a machine to pick out the important keywords amongst
+less important words or stop words) or simply use incorrect spelling.
+
 \chapter{State of the Art in Linked Data}
+\label{stateoftheart}
 

### 2014-04-28 paper.tex
Finished first chapter and made some headway with the second.

@@
 \documentclass[10pt,a4paper]{report}
+
+\usepackage{mathtools}
 
@@
 This report proposes improvements to the BBC Search product making use
-of \emph{Linked Data} \cite{bizer2009linked} and/or the Semantic Web
-\cite{berners2001semantic}. I hope to be able to demonstrate five tangible
+of \emph{Linked Data}\cite{bizer2009linked} and/or the Semantic
+Web\cite{berners2001semantic}. I hope to be able to demonstrate five tangible
 benefits this domain can bring to a search application, namely:
@@
   \item Further decoupling of BBC applications, which aids scalability,
-    maintainability and resilience in many software architectures. \cite{}
+    maintainability and resilience in many software architectures.\cite{}
   \item Improvements to the search results page that help users determine
-    if the results given are relevant via so-called \emph{Rich Snippets}
+    if the results given are relevant via so-called
+    \emph{Rich Snippets}\cite{goel2009introducing}
     that can automatically display some semantic information about a given
@@
   \item User experience and design improvements to the search results
-    where semantic properties about the results can drive visual sugar
+    where semantic properties about the results can drive visual decoration
     and calls to action, which can allow for a more flexible and
@@
 to enable users to search for and navigate all areas of the site using
-free-text queries. This might aid visitors who are unable to find their desired
+free text queries. This might aid visitors who are unable to find their desired
 content via other global or site-specific navigation or those who are simply
@@
 The general strategy is to perform
-any expensive transformation, expansion or ordering of the indexed
+any expensive transformation, expansion or ordering of data
 at index time so that query time algorithms may be optimised to
@@
 BBC content from a variety of sources and then needs to serve
-a diverse set of use cases. \cite{fenning2014applicability} The
+a diverse set of use cases.\cite{fenning2014applicability} The
 need to integrate against different data sources and funnel
@@
 transform and normalise data. Such patterns are notably
-summarised by Hohpe and Woolf\cite{hohpe2004enterprise}.
+summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}
 
@@
 what times they are available to watch on iPlayer, what kinds of devices
-are permitted by rights to watch them on iPlayer). This has challenges
-for providing a consistent and meaningful user experience across such
+are permitted by rights to watch them on iPlayer). There are challenges
+in providing a consistent and meaningful user experience across such
 a heterogeneous mix of content.
@@
 API through which all content is fed into the Search application. However,
-it varies based on practicalities whether
-work is done by the owners of the content to send content to the API
-or whether the developers of the Search application need to integrate
-existing feeds via an adapter pattern. Some pages on the BBC website no
+some integration work needs to be
+done by either the owners of the content to send content to the API
+or the developers of the Search application, who can integrate
+existing feeds via an adapter pattern.
+
+Some pages on the BBC website no
 longer have a dedicated team maintaining them and can sometimes only
@@
 content management systems, which can be collectively described as part
-of the so-called \emph{deep web}. \cite{}
+of the so-called \emph{deep web}.\cite{}
 
@@
 problem the linked data domain seeks to solve.
-
-% Do we need this?
-Concepts central to the information retrieval domain such as creating
-tokenisation, stemming, lemmatisation and relevance
-algorithms can normally be delegated to
-third party proprietary or free software. It is still useful however
-for developers of full search application to be aware of these concepts even
-if their implementation is abstracted away. Tokenisation, stemming and
-lemmatisation are index time concerns, the full definitions of which
-are out of scope for this report. In short, we want a search application
-to understand individual words within an article and to understand that, for
-example, ``mice'' and ``mouse'' are approximately the same word as well
-as verb forms like ``swim'', ``swam'', ``swum'' and ``swimming'' all being
-equivalent in the context of keyword retrieval.
 
@@
 
-\begin{equation}
-  precision = \quot{|{relevant documents}\and{retrieved documents}|}{|{retrieved documents}|}
-\end{equation}
+\begin{displaymath}
+  \textbf{precision} = \frac{
+    |\text{relevant documents} \cap \text{retrieved documents}|
+  }{
+    |\text{retrieved documents}|
+  }
+\end{displaymath}
 
-\begin{equation}
-  recall = \quot{|{relevant documents}\and{retrieved documents}|}{|{relevant documents}|}
-\end{equation}
+\begin{displaymath}
+  \textbf{recall} = \frac{
+    |{relevant documents} \cap \text{retrieved documents}|
+  }{
+    |\text{relevant documents}|
+  }
+\end{displaymath}
 
@@
 results, but such a system would perform poorly in terms of precision. A
-measure known as \emph{F-measure} was derived by van Rijsbergen \cite{} which
-balances precision recall based on preferring recall over precision \beta
+measure known as \emph{F-measure} was derived by van Rijsbergen
+\cite{rijsbergen1979information} which
+balances precision recall based on preferring recall over precision $\beta$
 times:
 
-% TODO: equation
+$$F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}$$
 
@@
 application can be evaluated quantitatively by these measures and more. A more
-qualitatively summary from the perspective of the end users could be:
+qualitative summary from the perspective of the end users could be:
 
@@
 relevant pages for those queries. For instance, a search for a city such
-as Coventry might naturally return recent news articles that mention the
+as \emph{Coventry} might naturally return recent news articles that mention the
 city (since news results are biased towards more recent articles over older
 ones), but the Editor's Choice links on top of the so-called \emph{organic
-results} can persistently offer users links for common use cases such as
+results} can persistently offer links for common use cases such as
 the BBC Weather page for Coventry.
@@
 One challenge for the querying of a search application is to be tolerant
-of variable quality of user-entered queries. Many users of web search
+of the variable quality of user-entered queries. Many users of web search
 engines may give ambiguously short queries, overly long queries with (where
 it can be hard for a machine to pick out the important keywords amongst
-less important words or stop words) or simply use incorrect spelling.
+less important words or stop words\cite{rajaraman2011data})
+or simply use incorrect spelling.
 
-\chapter{State of the Art in Linked Data}
+This problem can be ameliorated with a plethora of algorithm
+server-side solutions (e.g. spell checking), but a simple solution that
+can be implemented on the user interface is an \emph{autocomplete}
+or \emph{autosuggest} feature. The former prompts for potential
+queries, titles, names, etc. that they may be typing so as to prevent
+the need to type the query out in full. The latter feature can go
+further to suggest onwards journeys that bypass the need for a
+page of search results altogether.
+
+The search box for BBC Search implements an autocomplete
+feature -- known
+as \emph{Search Suggest} -- whereby
+the full names or titles of are suggested to users as they type the first
+few characters of their queries. This helps guide users into free text
+queries that are more likely to match terms in the indexes and reduces
+mismatching due to misspellings or otherwise poorly-formed queries.
+
+The list of suggestions that might surface in this system are
+currently chosen and maintained by hand by editorial staff. If a new
+concept breaks into the news (such as a notable person becoming notable
+for the first time), then a person must enter that term into the system.
+Similarly, if something should not be suggested to users any longer
+(perhaps for legal reasons or simply because it is no longer a relevant
+concept), then it must be amended or removed manually.
+
+This manual maintenance of the suggestion list also leads to a
+disconnect between searchable content and suggested queries that might
+appear as users type. There is an onus on editorial staff to ensure
+that content will be found when a suggested query is used. It might
+serve the website users better to find mechanisms by which to generate
+a useful set of suggestions from the corpus of content as it is
+indexed. The heterogenous nature of BBC content turns this into
+further integration work where different business rules are likely required
+to generate suggestions from different types of content.
+
+In chapter~\ref{stateoftheart} I will briefly outline some of the state of the
+art in the Linked Data domain and start to highlight areas that show
+the most promise for improving the four areas of the search application
+described in this chapter.
+
+\chapter{Linked Data}
 \label{stateoftheart}
+
+\section{Linked Data Principles}
+
+The concept of Linked Data can well be summarised as a representation of
+data that follows four principles:\cite{berners2011linked}
+
+\begin{enumerate}
+  \item Use URIs to denote things.
+  \item Prefer HTTP URIs (i.e. URLs) so that these things can be looked
+    up (i.e. \emph{dereferenced}.
+  \item When these URIs are dereferenced, provide useful information about
+    those things using standards.
+  \item Include links to other things (using their URIs) when such
+    information is published on the web.
+\end{enumerate}
 
@@
 
-\bibliographystyle{cell}
+\bibliographystyle{plain}
 \bibliography{bibtex}

### 2014-04-30 paper.tex
Some more work on the second chapter.

@@
 
-$$F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}$$
+\begin{displaymath}
+  F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}
+\end{displaymath}
 
@@
 
-\section{Linked Data Principles}
-
 The concept of Linked Data can well be summarised as a representation of
@@
 \end{enumerate}
+
+It can be seen as a subset of Semantic Web techniques and it builds upon
+the \emph{Resource Description Framework} (RDF)\cite{lassila1999resource},
+which is a general-purpose method for describing and modelling information.
+
+In this chapter, I will outline how web authors are encouraged to publish
+linked data within their content and how that is already used to enhance
+search results in global search engines. I will then introduce how linked
+data may be used within an enterprise setting to reduce traditional
+integration efforts and then touch on some other aspects of the linked
+data domain that could be of interest to the search application.
+
+\section{Publishing Linked Data within Web Pages}
+
+The Semantic Web movement has long recommended an approach of embedding
+RDF data models within web pages and documents using RDFa\cite{adida2012rdfa}
+and RDFa Lite\cite{lite2004rdfa}.
+
+\section{Enhancing Search Engine Results}
 
@@
 of semantic web technologies on the programmes microsites, Nature and BBC
-Music \cite{}, but indicate that some level of metadata can be retrieved
+Music \cite{raimond2010use}, but indicate that some level of metadata
+can be retrieved
 as linked data. In cases where the metadata are rich enough, it might be
@@
 integration.
+
+\section{Reasoning and Inference}
 

### 2014-05-02 paper.tex
Some reworking around bit on RDFa.

@@
 
-The Semantic Web movement has long recommended an approach of embedding
-RDF data models within web pages and documents using RDFa\cite{adida2012rdfa}
-and RDFa Lite\cite{lite2004rdfa}.
+Whilst there exist multiple formats for publishing RDF purely for machines
+(e.g. Turtle\cite{world2014rdf}, N-Triples, JSON-LD\cite{world2014json},
+N3, RDF/XML) there are multiple ways to embed semantic or linked data within
+an HTML web page:
+
+\begin{itemize}
+  \item RDFa\cite{adida2012rdfa} and RDFa Lite\cite{lite2004rdfa}.
+  \item DC-HTML defines how to embed the Dublin Core vocabulary within HTML
+    meta tags.
+\end{itemize}
 

### 2014-05-04 chapter1.tex
Updated makefile to give a word count after building PDF. Made some good progress with chapter 2 which is nearly completion. Also broke each chapter out into its own tex file to make it easier to manage. This has given a nice fringe benefit of being able to report word count broken down by chapter.

--- 2014-04-28 paper.tex
@@
-\documentclass[10pt,a4paper]{report}
-
-\usepackage{mathtools}
-
-\title{Proposal to improve BBC Search through the use of Linked Data}
-\author{Ross Fenning}
-
-\begin{document}
-
-\maketitle
-
 \chapter{Background}
@@
 described in this chapter.
-
-\chapter{Linked Data}
-\label{stateoftheart}
-
-\section{Linked Data Principles}
-
-The concept of Linked Data can well be summarised as a representation of
-data that follows four principles:\cite{berners2011linked}
-
-\begin{enumerate}
-  \item Use URIs to denote things.
-  \item Prefer HTTP URIs (i.e. URLs) so that these things can be looked
-    up (i.e. \emph{dereferenced}.
-  \item When these URIs are dereferenced, provide useful information about
-    those things using standards.
-  \item Include links to other things (using their URIs) when such
-    information is published on the web.
-\end{enumerate}
-
-\section{Linked Enterprise Data}
-
-In recent years, a growing trend has emerged to use
-\emph{Linked Data} in the enterprise to remove the need
-for repeated integration projects or data warehousing.
-\cite{allemang2010semantic} If we view the indexing processes
-of a search application as a variant of data warehousing,
-we can start to argue for enterprise-wide publishing of
-linked data as a more cost effective means of building search
-indexes over bespoke integration efforts.
-
-An important consideration is that BBC Search is largely directing
-users to public pages on the BBC website, a large number of which have
-already published some of their metadata as linked data. Notably, BBC News,
-BBC Sport and BBC Food all use some combination
-of microformats, microdata, RDFa, HTML meta tags within their HTML content
-pages. Some of this was to improve search results in external search engines
-such as Google and some of it ties into Facebook's Open Graph Protocol, which
-enables and enhances social media sharing of the pages.
-
-These efforts are not as structured and rich as the more notable uses
-of semantic web technologies on the programmes microsites, Nature and BBC
-Music \cite{}, but indicate that some level of metadata can be retrieved
-as linked data. In cases where the metadata are rich enough, it might be
-possible to avoid direct integration with databases, hidden back end
-web services and other structured ``feeds'' typically set up for enterprise
-integration.
-
-\chapter{Analysis}
-
-\chapter{Proposal}
-
-\chapter{Implementation Plan}
-
-\chapter{Summary}
-
-\bibliographystyle{plain}
-\bibliography{bibtex}
-
-\end{document}

### 2014-05-04 chapter2.tex
Updated makefile to give a word count after building PDF. Made some good progress with chapter 2 which is nearly completion. Also broke each chapter out into its own tex file to make it easier to manage. This has given a nice fringe benefit of being able to report word count broken down by chapter.

--- 2014-05-02 paper.tex
@@
-\documentclass[10pt,a4paper]{report}
-
-\usepackage{mathtools}
-
-\title{Proposal to improve BBC Search through the use of Linked Data}
-\author{Ross Fenning}
-
-\begin{document}
-
-\maketitle
-
-\chapter{Background}
-
-This report proposes improvements to the BBC Search product making use
-of \emph{Linked Data}\cite{bizer2009linked} and/or the Semantic
-Web\cite{berners2001semantic}. I hope to be able to demonstrate five tangible
-benefits this domain can bring to a search application, namely:
-
-\begin{enumerate}
-  \item Further decoupling of BBC applications, which aids scalability,
-    maintainability and resilience in many software architectures.\cite{}
-  \item Improvements to the search results page that help users determine
-    if the results given are relevant via so-called
-    \emph{Rich Snippets}\cite{goel2009introducing}
-    that can automatically display some semantic information about a given
-    result without the need for manual curation.
-  \item User experience and design improvements to the search results
-    where semantic properties about the results can drive visual decoration
-    and calls to action, which can allow for a more flexible and
-    adaptable design without the need to enumerate all ``kinds'' with
-    different templates.
-  \item Removal of the manual curation of the ``Editor's Choice'' results
-    against a given query and replacing it with curated linked data that
-    can provide recommended content against queries in a more general
-    manner.
-  \item Replacement of the manual curation of autocomplete suggestions
-    in the \emph{Search Suggest} service -- that suggests full text queries
-    as the user types -- with suggestions driven from linked data.
-\end{enumerate}
-
-In the rest of this chapter, I will give an overview of what role BBC
-Search plays and how we can usefully view the system as four
-distinct subsystems. In later chapters we can then look to improve these
-four separate systems one at a time and then evaluate how these improvements
-might complement each other.
-
-\section{BBC Search}
-
-BBC Search is an online product that forms part of the BBC website
-to enable users to search for and navigate all areas of the site using
-free text queries. This might aid visitors who are unable to find their desired
-content via other global or site-specific navigation or those who are simply
-looking for things that fall below the radar of the latest, greatest or
-otherwise promoted content.
-
-General-purpose search engines such as Google are also capable of directing
-users to BBC pages via free text queries, but there is a benefit the BBC
-can bring with its own search service that has greater knowledge of the
-BBC's own content. The BBC can use internal knowledge to predict a user's
-intent (e.g. if the query matches a programme title, then show links to watch
-the latest episode on iPlayer) or to provide editorially-curated
-links to significant pages (e.g. if a user searches for a term
-related to a major, ongoing news theme, curated links can
-link to an overview or FAQ for that ongoing event for those
-looking for the background on it).
-
-It is well established that a classical information retrieval system
-can be expressed as two sets of computation: processing of information
-into indexes (also known as \emph{indexing}) for quicker retrieval
-and the retrieval of documents from those indexes based on a user's
-query. These can be known as \emph{index time} or \emph{query time}
-processing respectively.
-
-The general strategy is to perform
-any expensive transformation, expansion or ordering of data
-at index time so that query time algorithms may be optimised to
-run as quickly as possible. This is an approach that has only
-increased in importance as information retrieval systems have moved
-from standalone systems (e.g. a catalogue search situated within
-a library used by a handful of users at once) to web-based
-searches across a far larger corpus with tens or even hundreds of
-users submitting queries in a single second.
-
-In the remaining sections of this chapter, I outline the considerations
-around these two sides of the search application in addition to the
-two complementary systems known as \emph{Editor's Choice} and
-\emph{Search Suggest}.
-
-\section{Indexing Content}
-
-The Search application needs to read in or receive metadata about
-BBC content from a variety of sources and then needs to serve
-a diverse set of use cases.\cite{fenning2014applicability} The
-need to integrate against different data sources and funnel
-that information into a common set of search indexes can
-typically be seen as an \emph{enterprise integration}
-problem. Architectural patterns have been developed, tested and
-implemented in a large number of enterprises to synchronise,
-transform and normalise data. Such patterns are notably
-summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}
-
-Some of the data is fairly flat, textual content such as articles and some
-information -- such as programmes -- is very structured (e.g. programmes,
-series, episodes, times of broadcast, channel on which they are broadcast,
-what times they are available to watch on iPlayer, what kinds of devices
-are permitted by rights to watch them on iPlayer). There are challenges
-in providing a consistent and meaningful user experience across such
-a heterogeneous mix of content.
-
-We can achieve some uniformity of the data by building a single, common
-API through which all content is fed into the Search application. However,
-some integration work needs to be
-done by either the owners of the content to send content to the API
-or the developers of the Search application, who can integrate
-existing feeds via an adapter pattern.
-
-Some pages on the BBC website no
-longer have a dedicated team maintaining them and can sometimes only
-be discovered via a web crawl as an external search engine would do. A lot
-of metadata about content also lives in a diverse range of databases and
-content management systems, which can be collectively described as part
-of the so-called \emph{deep web}.\cite{}
-
-In chapter~\ref{stateoftheart}, we will discuss how the deep web is one
-problem the linked data domain seeks to solve.
-
-\section{Retrieving Content}
-
-Once we have constructed an index optimised for keyword-based retrieval,
-we can begin to run queries against that index. A retrieval problem
-can be summarised as trying to maximise two separate measures: \emph{precision}
-and \emph{recall}, where:
-
-\begin{displaymath}
-  \textbf{precision} = \frac{
-    |\text{relevant documents} \cap \text{retrieved documents}|
-  }{
-    |\text{retrieved documents}|
-  }
-\end{displaymath}
-
-\begin{displaymath}
-  \textbf{recall} = \frac{
-    |{relevant documents} \cap \text{retrieved documents}|
-  }{
-    |\text{relevant documents}|
-  }
-\end{displaymath}
-
-Namely, precision is the fraction of the retrieved documents that were
-relevant to the user's query and recall is the fraction of documents out of
-all possible, relevant documents that appear in the search results.
-
-Note that a system could trivially maximise recall by always returning all
-results, but such a system would perform poorly in terms of precision. A
-measure known as \emph{F-measure} was derived by van Rijsbergen
-\cite{rijsbergen1979information} which
-balances precision recall based on preferring recall over precision $\beta$
-times:
-
-\begin{displaymath}
-  F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}
-\end{displaymath}
-
-There are other measures such as average precision and average mean precision
-that take into account ordering of results and the average over multiple
-queries respectively. A successful algorithm or third party search engine
-application can be evaluated quantitatively by these measures and more. A more
-qualitative summary from the perspective of the end users could be:
-
-\begin{quote}
-  A successful search application will return only the content the user wants
-  (precision) --
-  as high up the results list as possible -- and as much of desired content
-  as possible (recall).
-\end{quote}
-
-The set of all documents that could be retrieved by a query is known as the
-\emph{corpus} and search systems will typically apply a \emph{score} against
-each that gives some measure of confidence of the relevance of each document
-given a particular query. It should be noted that scores are a relative
-metric only and only have meaning within the context of a particular
-retrieval algorithm and particular query.
-
-\section{Editor's Choice}
-
-The current BBC Search application returns an ordered list of results
-for queries based on keyword matching within the titles, text or other
-chosen metadata fields as appropriate. However, there are cases where
-the algorithms employed may not return something noted as the official
-or canonical match for a concept, person, programme, etc. (e.g. the
-official microsite for a popular BBC programme or a profile page for
-a notable person on BBC News).
-
-Editorial staff thus have control over a curation system that manifests
-as an \emph{Editor's Choice} feature that will ensure the top one to three
-results for popular queries link to manually-chosen pages deemed as the most
-relevant pages for those queries. For instance, a search for a city such
-as \emph{Coventry} might naturally return recent news articles that mention the
-city (since news results are biased towards more recent articles over older
-ones), but the Editor's Choice links on top of the so-called \emph{organic
-results} can persistently offer links for common use cases such as
-the BBC Weather page for Coventry.
-
-Each and every link promoted within this feature is hand-chosen by editorial
-staff and much manual effort is needed to keep promoting new concepts
-as they appear and to remove pages as they get superseded. It is hoped
-in this proposal we can reduce some of that manual curation through the use
-of linked data and demonstrate ways editorial staff can focus on curating
-their own linked data such that Editor's Choice could evolve into a more
-generalised and automated subsystem. A metadata-driven curation system
-could use common patterns in the data to promote orders of magnitude more
-top links with a fraction of the current effort.
-
-\section{Search Suggest}
-
-One challenge for the querying of a search application is to be tolerant
-of the variable quality of user-entered queries. Many users of web search
-engines may give ambiguously short queries, overly long queries with (where
-it can be hard for a machine to pick out the important keywords amongst
-less important words or stop words\cite{rajaraman2011data})
-or simply use incorrect spelling.
-
-This problem can be ameliorated with a plethora of algorithm
-server-side solutions (e.g. spell checking), but a simple solution that
-can be implemented on the user interface is an \emph{autocomplete}
-or \emph{autosuggest} feature. The former prompts for potential
-queries, titles, names, etc. that they may be typing so as to prevent
-the need to type the query out in full. The latter feature can go
-further to suggest onwards journeys that bypass the need for a
-page of search results altogether.
-
-The search box for BBC Search implements an autocomplete
-feature -- known
-as \emph{Search Suggest} -- whereby
-the full names or titles of are suggested to users as they type the first
-few characters of their queries. This helps guide users into free text
-queries that are more likely to match terms in the indexes and reduces
-mismatching due to misspellings or otherwise poorly-formed queries.
-
-The list of suggestions that might surface in this system are
-currently chosen and maintained by hand by editorial staff. If a new
-concept breaks into the news (such as a notable person becoming notable
-for the first time), then a person must enter that term into the system.
-Similarly, if something should not be suggested to users any longer
-(perhaps for legal reasons or simply because it is no longer a relevant
-concept), then it must be amended or removed manually.
-
-This manual maintenance of the suggestion list also leads to a
-disconnect between searchable content and suggested queries that might
-appear as users type. There is an onus on editorial staff to ensure
-that content will be found when a suggested query is used. It might
-serve the website users better to find mechanisms by which to generate
-a useful set of suggestions from the corpus of content as it is
-indexed. The heterogenous nature of BBC content turns this into
-further integration work where different business rules are likely required
-to generate suggestions from different types of content.
-
-In chapter~\ref{stateoftheart} I will briefly outline some of the state of the
-art in the Linked Data domain and start to highlight areas that show
-the most promise for improving the four areas of the search application
-described in this chapter.
-
 \chapter{Linked Data}
@@
 \section{Publishing Linked Data within Web Pages}
+\label{publishing-linked-data}
 
@@
     meta tags.
+  \item Microdata is an HTML standard that allows annotating existing markup
+    via additional attributes so that it serves as metadata in addition to
+    its purpose as text for humans.
+  \item Microformats are another mechanism that embeds semantic metadata
+    within existing HTML tags and attributes.
 \end{itemize}
 
+Using one or more of these approaches allows a publisher to convey
+machine-readable metadata in the same document that is served to humans.
+This allows, for example, search engines to index more categorical and
+structured information about a page when it is crawled in addition to the
+normal processing on the text content. This was the foundation of the
+Semantic Web\cite{berners2001semantic} before the term Linked Data
+emerged and the aspiration was that widespread adoption would lead to
+a comprehensive ``Web of Data'' to rival the rich, so-called
+``Web of Documents'' that is the World Wide Web as we know it as a collection
+of human-readable pages.
+
+People such as Hepp have argued against adding markup such as RDFa around
+the text visible to humans and instead adding hidden, additional markup to
+contain semantic information.\cite{hepp2009rdf2rdfa} Hepp argues that
+this allows the HTML tree structure to be decoupled from the data structure
+of the vocabulary in use, although it does introduce redundancy if all
+semantic information is duplicated in both human- and machine-readable forms.
+
+Google have seemingly partially adopted an approach following this principle
+-- at least for web authors publishing information about music
+events.\cite{googlejsonld} Google are piloting embedding RDF metadata in
+\emph{JSON-LD} format within HTML \texttt{<script>} tags to add semantic
+information alongside textual data, but without annotating this metadata
+around the textual content itself as we would with RDFa, for example.
+
+All of the above approaches can be found ``in the wild'' in pages across
+the Web with differing rates of adoption. General-purpose web search
+engines can make use of this additional metadata to improve the quality
+of the search results in a number of ways. In section~\ref{enhancing-results},
+I discuss some of these potential improvements.
+
 \section{Enhancing Search Engine Results}
+\label{enhancing-results}
+
+There are at least two key ways in which a search application might
+improve the quality of results by making use of semantic metadata as
+described in section~\ref{publishing-linked-data}.
+
+One approach is to allow
+user queries to be matched against metadata properties in addition
+to the text, perhaps with higher precedence. This may lead to a search
+engine that seems ``intelligent'' enough not just to retrieve articles
+by keywords found therein, but also by keywords that match related
+concepts and properties.
+
+For example, a page about a film might be retrieved
+by matching names of actors that appeared in the film, even if that actor's
+name does not appear in any textual information -- e.g. the synopsis --
+that appears on the page. If the author has published semantic metadata
+within the the film's page to list all the actors and other contributors,
+then our search application can match on this auxiliary information.
+
+Whilst this technique could improve the relevance of the results for a
+given query (and consequently improve the precision of the system for that
+particular query), a second technique known as \emph{Rich Snippets} improves
+results from a usability perspective by aiding users in assessing whether
+a result is relevant or not.
+
+Rich Snippets are a distinct improvement 
+to the user experience and information architecture
+of search applications. A search engine results page (sometimes known as a
+\emph{SERP}) may well retrieve almost all relevant results for a query -- and
+achieve nearly one hundred percent precision -- but this high performance
+is lost on a human user if the results are presented in a form where it is
+hard to determine the respective relevant of each result.
 
@@
 \section{Reasoning and Inference}
-
-\chapter{Analysis}
-
-\chapter{Proposal}
-
-\chapter{Implementation Plan}
-
-\chapter{Summary}
-
-\bibliographystyle{plain}
-\bibliography{bibtex}
-
-\end{document}

### 2014-05-04 paper.tex
Updated makefile to give a word count after building PDF. Made some good progress with chapter 2 which is nearly completion. Also broke each chapter out into its own tex file to make it easier to manage. This has given a nice fringe benefit of being able to report word count broken down by chapter.

--- 2014-04-28 paper.tex
@@
 
+\usepackage{nag}
 \usepackage{mathtools}
+\usepackage{natbib}
+\usepackage{url}
 
@@
 
-\chapter{Background}
-
-This report proposes improvements to the BBC Search product making use
-of \emph{Linked Data}\cite{bizer2009linked} and/or the Semantic
-Web\cite{berners2001semantic}. I hope to be able to demonstrate five tangible
-benefits this domain can bring to a search application, namely:
-
-\begin{enumerate}
-  \item Further decoupling of BBC applications, which aids scalability,
-    maintainability and resilience in many software architectures.\cite{}
-  \item Improvements to the search results page that help users determine
-    if the results given are relevant via so-called
-    \emph{Rich Snippets}\cite{goel2009introducing}
-    that can automatically display some semantic information about a given
-    result without the need for manual curation.
-  \item User experience and design improvements to the search results
-    where semantic properties about the results can drive visual decoration
-    and calls to action, which can allow for a more flexible and
-    adaptable design without the need to enumerate all ``kinds'' with
-    different templates.
-  \item Removal of the manual curation of the ``Editor's Choice'' results
-    against a given query and replacing it with curated linked data that
-    can provide recommended content against queries in a more general
-    manner.
-  \item Replacement of the manual curation of autocomplete suggestions
-    in the \emph{Search Suggest} service -- that suggests full text queries
-    as the user types -- with suggestions driven from linked data.
-\end{enumerate}
-
-In the rest of this chapter, I will give an overview of what role BBC
-Search plays and how we can usefully view the system as four
-distinct subsystems. In later chapters we can then look to improve these
-four separate systems one at a time and then evaluate how these improvements
-might complement each other.
-
-\section{BBC Search}
-
-BBC Search is an online product that forms part of the BBC website
-to enable users to search for and navigate all areas of the site using
-free text queries. This might aid visitors who are unable to find their desired
-content via other global or site-specific navigation or those who are simply
-looking for things that fall below the radar of the latest, greatest or
-otherwise promoted content.
-
-General-purpose search engines such as Google are also capable of directing
-users to BBC pages via free text queries, but there is a benefit the BBC
-can bring with its own search service that has greater knowledge of the
-BBC's own content. The BBC can use internal knowledge to predict a user's
-intent (e.g. if the query matches a programme title, then show links to watch
-the latest episode on iPlayer) or to provide editorially-curated
-links to significant pages (e.g. if a user searches for a term
-related to a major, ongoing news theme, curated links can
-link to an overview or FAQ for that ongoing event for those
-looking for the background on it).
-
-It is well established that a classical information retrieval system
-can be expressed as two sets of computation: processing of information
-into indexes (also known as \emph{indexing}) for quicker retrieval
-and the retrieval of documents from those indexes based on a user's
-query. These can be known as \emph{index time} or \emph{query time}
-processing respectively.
-
-The general strategy is to perform
-any expensive transformation, expansion or ordering of data
-at index time so that query time algorithms may be optimised to
-run as quickly as possible. This is an approach that has only
-increased in importance as information retrieval systems have moved
-from standalone systems (e.g. a catalogue search situated within
-a library used by a handful of users at once) to web-based
-searches across a far larger corpus with tens or even hundreds of
-users submitting queries in a single second.
-
-In the remaining sections of this chapter, I outline the considerations
-around these two sides of the search application in addition to the
-two complementary systems known as \emph{Editor's Choice} and
-\emph{Search Suggest}.
-
-\section{Indexing Content}
-
-The Search application needs to read in or receive metadata about
-BBC content from a variety of sources and then needs to serve
-a diverse set of use cases.\cite{fenning2014applicability} The
-need to integrate against different data sources and funnel
-that information into a common set of search indexes can
-typically be seen as an \emph{enterprise integration}
-problem. Architectural patterns have been developed, tested and
-implemented in a large number of enterprises to synchronise,
-transform and normalise data. Such patterns are notably
-summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}
-
-Some of the data is fairly flat, textual content such as articles and some
-information -- such as programmes -- is very structured (e.g. programmes,
-series, episodes, times of broadcast, channel on which they are broadcast,
-what times they are available to watch on iPlayer, what kinds of devices
-are permitted by rights to watch them on iPlayer). There are challenges
-in providing a consistent and meaningful user experience across such
-a heterogeneous mix of content.
-
-We can achieve some uniformity of the data by building a single, common
-API through which all content is fed into the Search application. However,
-some integration work needs to be
-done by either the owners of the content to send content to the API
-or the developers of the Search application, who can integrate
-existing feeds via an adapter pattern.
-
-Some pages on the BBC website no
-longer have a dedicated team maintaining them and can sometimes only
-be discovered via a web crawl as an external search engine would do. A lot
-of metadata about content also lives in a diverse range of databases and
-content management systems, which can be collectively described as part
-of the so-called \emph{deep web}.\cite{}
-
-In chapter~\ref{stateoftheart}, we will discuss how the deep web is one
-problem the linked data domain seeks to solve.
-
-\section{Retrieving Content}
-
-Once we have constructed an index optimised for keyword-based retrieval,
-we can begin to run queries against that index. A retrieval problem
-can be summarised as trying to maximise two separate measures: \emph{precision}
-and \emph{recall}, where:
-
-\begin{displaymath}
-  \textbf{precision} = \frac{
-    |\text{relevant documents} \cap \text{retrieved documents}|
-  }{
-    |\text{retrieved documents}|
-  }
-\end{displaymath}
-
-\begin{displaymath}
-  \textbf{recall} = \frac{
-    |{relevant documents} \cap \text{retrieved documents}|
-  }{
-    |\text{relevant documents}|
-  }
-\end{displaymath}
-
-Namely, precision is the fraction of the retrieved documents that were
-relevant to the user's query and recall is the fraction of documents out of
-all possible, relevant documents that appear in the search results.
-
-Note that a system could trivially maximise recall by always returning all
-results, but such a system would perform poorly in terms of precision. A
-measure known as \emph{F-measure} was derived by van Rijsbergen
-\cite{rijsbergen1979information} which
-balances precision recall based on preferring recall over precision $\beta$
-times:
-
-$$F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}$$
-
-There are other measures such as average precision and average mean precision
-that take into account ordering of results and the average over multiple
-queries respectively. A successful algorithm or third party search engine
-application can be evaluated quantitatively by these measures and more. A more
-qualitative summary from the perspective of the end users could be:
-
-\begin{quote}
-A successful search application will return only the content the user wants
-(precision) --
-as high up the results list as possible -- and as much of desired content
-as possible (recall).
-\end{quote}
-
-The set of all documents that could be retrieved by a query is known as the
-\emph{corpus} and search systems will typically apply a \emph{score} against
-each that gives some measure of confidence of the relevance of each document
-given a particular query. It should be noted that scores are a relative
-metric only and only have meaning within the context of a particular
-retrieval algorithm and particular query.
-
-\section{Editor's Choice}
-
-The current BBC Search application returns an ordered list of results
-for queries based on keyword matching within the titles, text or other
-chosen metadata fields as appropriate. However, there are cases where
-the algorithms employed may not return something noted as the official
-or canonical match for a concept, person, programme, etc. (e.g. the
-official microsite for a popular BBC programme or a profile page for
-a notable person on BBC News).
-
-Editorial staff thus have control over a curation system that manifests
-as an \emph{Editor's Choice} feature that will ensure the top one to three
-results for popular queries link to manually-chosen pages deemed as the most
-relevant pages for those queries. For instance, a search for a city such
-as \emph{Coventry} might naturally return recent news articles that mention the
-city (since news results are biased towards more recent articles over older
-ones), but the Editor's Choice links on top of the so-called \emph{organic
-results} can persistently offer links for common use cases such as
-the BBC Weather page for Coventry.
-
-Each and every link promoted within this feature is hand-chosen by editorial
-staff and much manual effort is needed to keep promoting new concepts
-as they appear and to remove pages as they get superseded. It is hoped
-in this proposal we can reduce some of that manual curation through the use
-of linked data and demonstrate ways editorial staff can focus on curating
-their own linked data such that Editor's Choice could evolve into a more
-generalised and automated subsystem. A metadata-driven curation system
-could use common patterns in the data to promote orders of magnitude more
-top links with a fraction of the current effort.
-
-\section{Search Suggest}
-
-One challenge for the querying of a search application is to be tolerant
-of the variable quality of user-entered queries. Many users of web search
-engines may give ambiguously short queries, overly long queries with (where
-it can be hard for a machine to pick out the important keywords amongst
-less important words or stop words\cite{rajaraman2011data})
-or simply use incorrect spelling.
-
-This problem can be ameliorated with a plethora of algorithm
-server-side solutions (e.g. spell checking), but a simple solution that
-can be implemented on the user interface is an \emph{autocomplete}
-or \emph{autosuggest} feature. The former prompts for potential
-queries, titles, names, etc. that they may be typing so as to prevent
-the need to type the query out in full. The latter feature can go
-further to suggest onwards journeys that bypass the need for a
-page of search results altogether.
-
-The search box for BBC Search implements an autocomplete
-feature -- known
-as \emph{Search Suggest} -- whereby
-the full names or titles of are suggested to users as they type the first
-few characters of their queries. This helps guide users into free text
-queries that are more likely to match terms in the indexes and reduces
-mismatching due to misspellings or otherwise poorly-formed queries.
-
-The list of suggestions that might surface in this system are
-currently chosen and maintained by hand by editorial staff. If a new
-concept breaks into the news (such as a notable person becoming notable
-for the first time), then a person must enter that term into the system.
-Similarly, if something should not be suggested to users any longer
-(perhaps for legal reasons or simply because it is no longer a relevant
-concept), then it must be amended or removed manually.
-
-This manual maintenance of the suggestion list also leads to a
-disconnect between searchable content and suggested queries that might
-appear as users type. There is an onus on editorial staff to ensure
-that content will be found when a suggested query is used. It might
-serve the website users better to find mechanisms by which to generate
-a useful set of suggestions from the corpus of content as it is
-indexed. The heterogenous nature of BBC content turns this into
-further integration work where different business rules are likely required
-to generate suggestions from different types of content.
-
-In chapter~\ref{stateoftheart} I will briefly outline some of the state of the
-art in the Linked Data domain and start to highlight areas that show
-the most promise for improving the four areas of the search application
-described in this chapter.
-
-\chapter{Linked Data}
-\label{stateoftheart}
-
-\section{Linked Data Principles}
-
-The concept of Linked Data can well be summarised as a representation of
-data that follows four principles:\cite{berners2011linked}
-
-\begin{enumerate}
-  \item Use URIs to denote things.
-  \item Prefer HTTP URIs (i.e. URLs) so that these things can be looked
-    up (i.e. \emph{dereferenced}.
-  \item When these URIs are dereferenced, provide useful information about
-    those things using standards.
-  \item Include links to other things (using their URIs) when such
-    information is published on the web.
-\end{enumerate}
-
-\section{Linked Enterprise Data}
-
-In recent years, a growing trend has emerged to use
-\emph{Linked Data} in the enterprise to remove the need
-for repeated integration projects or data warehousing.
-\cite{allemang2010semantic} If we view the indexing processes
-of a search application as a variant of data warehousing,
-we can start to argue for enterprise-wide publishing of
-linked data as a more cost effective means of building search
-indexes over bespoke integration efforts.
-
-An important consideration is that BBC Search is largely directing
-users to public pages on the BBC website, a large number of which have
-already published some of their metadata as linked data. Notably, BBC News,
-BBC Sport and BBC Food all use some combination
-of microformats, microdata, RDFa, HTML meta tags within their HTML content
-pages. Some of this was to improve search results in external search engines
-such as Google and some of it ties into Facebook's Open Graph Protocol, which
-enables and enhances social media sharing of the pages.
-
-These efforts are not as structured and rich as the more notable uses
-of semantic web technologies on the programmes microsites, Nature and BBC
-Music \cite{}, but indicate that some level of metadata can be retrieved
-as linked data. In cases where the metadata are rich enough, it might be
-possible to avoid direct integration with databases, hidden back end
-web services and other structured ``feeds'' typically set up for enterprise
-integration.
-
-\chapter{Analysis}
-
-\chapter{Proposal}
-
-\chapter{Implementation Plan}
-
-\chapter{Summary}
+\include{chapter1}
+\include{chapter2}
+\include{chapter3}
+\include{chapter4}
+\include{chapter5}
+\include{chapter6}
 

### 2014-05-04 chapter2.tex
Nearing the end of chapter 2.

@@
 
+Evaluation of the effectiveness of search results enhanced with rich snippets
+via both explicit and implicit user feedback had been carried out by
+Haas et al.\cite{haas2011enhanced} at Microsoft and Yahoo! research. The
+results showed a promising preference from 84\% of users for a result
+with enhanced information with the most common downside being that the
+snippet may sometimes present incorrect information (e.g. showing the wrong
+price for a product is less preferable than simply not attempting to present
+the price at all). Implicit feedback via click-through rates (CTR) --
+a common metric to indicate that users are happy enough with the information
+given to click on the link given -- suggested users were more likely to
+follow enhanced results.
+
+A higher CTR for semantically-enhanced search results creates some pressure
+and incentive on web publishers to include semantic metadata in their web
+content if they aspire to attacting visitors via global search engines such
+as Google, Bing and Yahoo!.
+
+In section~\ref{linked-enterprise-data} and section~\ref{reasoning}, I will
+outline some of the linked data approaches and techniques that relate to
+working with data models themselves.
+
 \section{Linked Enterprise Data}
+\label{linked-enterprise-data}
 
@@
 \section{Reasoning and Inference}
+\label{reasoning}

### 2014-05-05 chapter1.tex
Drawing a line under chapter 2 for now so I can move on to the important stuff. I've not said anything around inference, but I probably don't need to.

@@
 typically be seen as an \emph{enterprise integration}
-problem. Architectural patterns have been developed, tested and
-implemented in a large number of enterprises to synchronise,
-transform and normalise data. Such patterns are notably
-summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}
+problem.
 
@@
 
-The current BBC Search application returns an ordered list of results
+`The current BBC Search application returns an ordered list of results
 for queries based on keyword matching within the titles, text or other

### 2014-05-05 chapter2.tex
Drawing a line under chapter 2 for now so I can move on to the important stuff. I've not said anything around inference, but I probably don't need to.

@@
 
+\emph{Enterprise integration} is an important technical field within the
+discipline of Enterprise Architecture that focuses on interconnecting
+systems and allowing data to flow between them. This can be seen as
+the practice of breaking down information silos that naturally emerge
+in enterprise organisations.\cite{allemang2010semantic}
+
+Architectural patterns have been developed, tested and
+implemented in a large number of enterprises to synchronise,
+transform and normalise data. Such patterns are notably
+summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}
+
+There are difficulties with some of these approaches noted by
+Allemang\cite{allemang2010semantic}. Data warehousing,
+integration projects and metadata repositories can all
+be time-consuming to implement, require repeated updating when
+use cases change and at the extreme can be seen as solving the
+problem of too many silos by adding another silo.
+
 In recent years, a growing trend has emerged to use
-\emph{Linked Data} in the enterprise to remove the need
+Linked Data in the enterprise to remove the need
 for repeated integration projects or data warehousing.
-\cite{allemang2010semantic} If we view the indexing processes
+indexes over bespoke integration efforts. This follows from
+a major motivation of Linked Data being that it aids in breaking
+down information silos. \cite{bizer2009linked} In the
+\emph{Linked Enterprise Data} approach, all information
+production remains \emph{distributed} but is
+\emph{connectable}.\cite{allemang2010semantic}
+
+An organisation that seeks to ensure that all information is
+published as Linked Data can learn from examples such as Wikipedia
+-- or indeed the web in general -- where individual experts are
+encouraged to share knowledge rather than keep it in silos. This
+distributed approach recognises that diversity and flux are the
+steady state of an agile enterprise. Two sources that happen
+to use the same vocabulary are instantly interoperable. Two
+sources that use a different vocabulary could well be integrated
+simply by creating appropriate mappings between the vocabularies.
+It should not be necessary to re-engineer a whole dataset nor
+create entirely new systems just for integration.
+
+There are still costs however in additional services, infrastructure
+and training in exposing data as linked data throughout the
+enterprise.\cite{hyland2010preparing} A practical approach
+has been suggested by Davis\cite{davis2011achieving} where enterprises
+can expose data via known formats such as Atom\cite{nottingham2005atom}
+and RESTful web services. Davis argues that the \texttt{atom:link}
+element offers some of the functionality of an RDF triple where
+an entity can be linked to other entities via the \texttt{href}
+attribute and the nature of that relationship is described by
+the \texttt{rel} attribute.
+
+The use of RESTful services and XML formats are very common in
+the enterprise -- noting however that many do not follow all tenets
+of the REST architectural style. This suggests that businesses
+could adopt the pattern suggested by Davis to expose their
+data across the organisation using technologies and techniques
+with which they are likely familiar. This eschews the full power
+of a stack based RDF, OWL and SPARQL, but might be a better
+opportunity for businesses that otherwise would not take on a
+Linked Data approach at all.  Many proponents of Linked Data would
+argue that the important aspect is that the data are exposed and
+linked, however that is achieved.
+
+\begin{comment}
+If we view the indexing processes
 of a search application as a variant of data warehousing,
@@
 linked data as a more cost effective means of building search
-indexes over bespoke integration efforts.
 
@@
 integration.
-
-\section{Reasoning and Inference}
-\label{reasoning}
+\end{comment}

### 2014-05-05 chapter3.tex
Drawing a line under chapter 2 for now so I can move on to the important stuff. I've not said anything around inference, but I probably don't need to.

\chapter{Analysis}

In this chapter, I will

\section{}

### 2014-05-05 chapter1.tex
Made some start to chapter 3 and proved getting graphviz working for embedded diagrams.

--- 2014-05-04 chapter1.tex
@@
 \chapter{Background}
+\label{intro}
 
@@
 
-The Search application needs to read in or receive metadata about
-BBC content from a variety of sources and then needs to serve
-a diverse set of use cases.\cite{fenning2014applicability} The
-need to integrate against different data sources and funnel
-that information into a common set of search indexes can
-typically be seen as an \emph{enterprise integration}
-problem. Architectural patterns have been developed, tested and
-implemented in a large number of enterprises to synchronise,
-transform and normalise data. Such patterns are notably
-summarised by Hohpe and Woolf.\cite{hohpe2004enterprise}
-
-Some of the data is fairly flat, textual content such as articles and some
-information -- such as programmes -- is very structured (e.g. programmes,
-series, episodes, times of broadcast, channel on which they are broadcast,
-what times they are available to watch on iPlayer, what kinds of devices
-are permitted by rights to watch them on iPlayer). There are challenges
-in providing a consistent and meaningful user experience across such
-a heterogeneous mix of content.
-
-We can achieve some uniformity of the data by building a single, common
-API through which all content is fed into the Search application. However,
-some integration work needs to be
-done by either the owners of the content to send content to the API
-or the developers of the Search application, who can integrate
-existing feeds via an adapter pattern.
-
-Some pages on the BBC website no
-longer have a dedicated team maintaining them and can sometimes only
-be discovered via a web crawl as an external search engine would do. A lot
-of metadata about content also lives in a diverse range of databases and
-content management systems, which can be collectively described as part
-of the so-called \emph{deep web}.\cite{}
-
-In chapter~\ref{stateoftheart}, we will discuss how the deep web is one
-problem the linked data domain seeks to solve.
+% TODO
 

### 2014-05-05 chapter3.tex
Made some start to chapter 3 and proved getting graphviz working for embedded diagrams.

@@
 
-In this chapter, I will
+In this chapter, I will give a deeper analysis of the four
+components of the search application identified in
+chapter~\ref{intro} and start to highlight areas where linked data
+approaches or semantic web technologies could have a r\^ole to play.
 
-\section{}
+\section{Indexing Content}
+
+\subsection{Overview}
+
+The Search application needs to read in or receive metadata about
+BBC content from a variety of sources and then needs to serve
+a diverse set of use cases.\cite{fenning2014applicability} The
+need to integrate against different data sources and funnel
+that information into a common set of search indexes can
+typically be seen as an \emph{enterprise integration}
+problem.
+
+Some of the data is fairly flat, textual content such as articles and some
+information -- such as programmes -- is very structured (e.g. programmes,
+series, episodes, times of broadcast, channel on which they are broadcast,
+what times they are available to watch on iPlayer, what kinds of devices
+are permitted by rights to watch them on iPlayer). There are challenges
+in providing a consistent and meaningful user experience across such
+a heterogeneous mix of content.
+
+We can achieve some uniformity of the data by building a single, common
+API through which all content is fed into the Search application. However,
+some integration work needs to be
+done by either the owners of the content to send content to the API
+or the developers of the Search application, who can integrate
+existing feeds via an adapter pattern.
+
+Some pages on the BBC website no
+longer have a dedicated team maintaining them and can sometimes only
+be discovered via a web crawl as an external search engine would do. A lot
+of metadata about content also lives in a diverse range of databases and
+content management systems, which may or may not be easily retrievable
+via the public web.
+
+\subsection{Current Implementation}
+
+\begin{dot2tex}[neato,options=-tmath]
+digraph G {
+    node [shape="circle"];
+    a_1 -> a_2 -> a_3 -> a_4 -> a_1;
+    }
+\end{dot2tex}
+
+\section{Search Results Page}
+
+\section{Editor's Choice}
+
+\section{Search Suggest}

### 2014-05-05 chapter2.tex
Made some start to chapter 3 and proved getting graphviz working for embedded diagrams.
Removed bad reference and started building up an abstract diagram of the indexing chain.

@@
 
-In section~\ref{linked-enterprise-data} and section~\ref{reasoning}, I will
-outline some of the linked data approaches and techniques that relate to
-working with data models themselves.
-
 \section{Linked Enterprise Data}
@@
 a major motivation of Linked Data being that it aids in breaking
-down information silos. \cite{bizer2009linked} In the
+down information silos.\cite{bizer2009linked} In the
 \emph{Linked Enterprise Data} approach, all information

### 2014-05-05 chapter3.tex
Removed bad reference and started building up an abstract diagram of the indexing chain.
Made a good start on chapter 3 and added a couple of diagrams.

@@
 that information into a common set of search indexes can
-typically be seen as an \emph{enterprise integration}
+typically be seen as an enterprise integration
 problem.
 
-Some of the data is fairly flat, textual content such as articles and some
+Some of the data are fairly flat, textual content such as articles and some
 information -- such as programmes -- is very structured (e.g. programmes,
@@
 
-\begin{dot2tex}[neato,options=-tmath]
-digraph G {
-    node [shape="circle"];
-    a_1 -> a_2 -> a_3 -> a_4 -> a_1;
+\begin{dot2tex}[dot,options=-tmath]
+digraph ingest {
+  rankdir=LR;
+
+  Programmes -> Dynamite
+  Dynamite -> FileBasedQueues
+
+  News -> CPS
+  Newsround -> CPS
+  Newsbeat -> CPS
+  Sport -> CPS  
+  CPS -> FileBasedQueues
+
+  MarketData -> FileBasedQueues
+
+  trans3 [label="Transformation"]
+  WorldService -> trans3
+  trans3 -> IngestAPI
+
+  ProgrammesWebsites -> Crawler
+  BBCFood -> Crawler
+  LegacyWebsites -> Crawler
+  trans2 [label="Transformation"]
+  Crawler -> trans2
+  trans2 -> IngestAPI
+
+  IngestAPI -> SearchIndexes
+
+  FileBasedQueues -> Transformation
+  Transformation -> SearchIndexes
 }
 \end{dot2tex}
+
+Figure 1 shows an informal view of the flow of information into the
+search indexes. Note that some content is transformed
+by integration applications written by the Search team whilst some
+is pushed via a so-called ``Ingest API''. This API ensures that
+all content is normalised to some common format and vocabulary before
+it is sent to the indexes. From the perspective of the search application
+system, this reduces the complexity of having to map multiple formats
+and vocabularies to the common representation.
+
+However, if we consider the holistic BBC online system, that transformation
+and integration work still needs to happen. It is arguably more efficient to
+push the integration efforts back onto the respective teams and domain experts
+in charge of each type of content, but that then puts burden on those teams
+to prioritise integrating with the search system over other work planned
+for their product. This is especially difficult again for content that no
+longer has a team actively maintaining it, which is shown by the need
+to transform all content found via the Crawler; there is no clear team to
+whom the transformation/integration could be delegated.
+
+It is clear that the search application has the need to normalise vocabularies
+to some extend (e.g. is it ``title'', ``headline'' or ``display title''
+that I should display as the link text on the results page?) and this requires
+some form of transformation. This frames the search application as being a
+key system whose primary r\^ole is to break down all the content silos in the
+BBC, which was noted as a motivation for Linked Data in chapter 2.
+
+There is also an apparent requirement that we are cautious of delegating
+too much integration work to other teams. From the perspective of teams
+whose products produce content, the ideal search system would be
+``light touch'' and reasonably passive at indexing their content. This
+expectation is strengthened by the long history of public, general-purpose
+web search engines such as Google who seem to find websites by themselves
+and index them without any input from webmasters. However, it should
+not be overlooked that Google does in fact place some burden on webmasters
+to increase the crawlability and indexability of their websites. This
+burden is welcomed due to the benefits of higher rankings that emerge
+after sinking those costs.
+
+Can the same be said that a particular web team
+in the BBC would welcome additional integration effort for the search system?
+Are there benefits that would justify their integration costs? Perhaps if
+these teams have already sunk the costs of optimising their content for
+Google, the search system can at least make use of these efforts and only
+require additional integration work if there are further benefits?
+
+\subsection{The Content}
+
+The front end search application currently divides all the searchable
+content into so-called ``zones'',
 

### 2014-05-05 chapter3.tex
Starting drilling into the different content items.

@@
 The front end search application currently divides all the searchable
-content into so-called ``zones'',
+content into so-called ``zones'':
+
+%TODO - is this all of them?
+\begin{itemize}
+  \item About the BBC
+  \item Blogs
+  \item CBBC
+  \item Films
+  \item Food
+  \item Gardening
+  \item Health \& Parenting 
+  \item History
+  \item iPlayer
+  \item Learning
+  \item Local (archive)
+  \item Music
+  \item News
+  \item Ouch!
+  \item Religion \& Ethics
+  \item Science \& Nature
+  \item Sport
+  \item Teenagers
+  \item TV \& Radio Programmes
+  \item TV \& Radio Sites
+\end{itemize}
+
+Some of these zones or categories related to major, well-known areas of
+BBC online. Some seem to be more esoteric or legacy areas, many of which
+are obtained through a web crawler. The presence of ``iPlayer'',
+``TV \& Radio Programmes'' and ``TV & Radio Sites'' is a distinction that
+has arisen for technical and historic reasons, which is not likely to be
+clear to users.
+
+In the rest of this section, I will look at the nature of each category
+of content, how it is currently collected for indexing and note any
+obvious areas that might benefit from an improved approach to indexing.
+
+\subsection{About the BBC}
+
+The ``About the BBC'' category is a collection of subsites centred out
+information about the BBC itself. Audience members can here find information
+about making complaints, press releases, news about the BBC, blogs, etc.
+
+This can be content that users will want to find via the search application.
+The BBC homepage is focused around presented latest online content, but it
+is with these more fringe areas of the BBC website that satisfy specific
+needs (e.g. ``How do I complain about a programme?'') that the
+search application can be of particular use.
+
+There is a mix of static pages and time-based content such as blog posts.
+One advantage of any part of the BBC website that hosts posts or articles,
+is they are generally syndicated via RSS or Atom. This gives an opportunity
+to follow for new updates in the same way the public would without any
+need for bespoke integration work by the teams in charge of the content.
 

### 2014-05-06 chapter1.tex
Slow progress with chapter3 and moved some stuff from chapter 1 as that's still too long.

@@
 
-Each and every link promoted within this feature is hand-chosen by editorial
-staff and much manual effort is needed to keep promoting new concepts
-as they appear and to remove pages as they get superseded. It is hoped
-in this proposal we can reduce some of that manual curation through the use
-of linked data and demonstrate ways editorial staff can focus on curating
-their own linked data such that Editor's Choice could evolve into a more
-generalised and automated subsystem. A metadata-driven curation system
-could use common patterns in the data to promote orders of magnitude more
-top links with a fraction of the current effort.
-
 \section{Search Suggest}
@@
 
-The list of suggestions that might surface in this system are
-currently chosen and maintained by hand by editorial staff. If a new
-concept breaks into the news (such as a notable person becoming notable
-for the first time), then a person must enter that term into the system.
-Similarly, if something should not be suggested to users any longer
-(perhaps for legal reasons or simply because it is no longer a relevant
-concept), then it must be amended or removed manually.
-
-This manual maintenance of the suggestion list also leads to a
-disconnect between searchable content and suggested queries that might
-appear as users type. There is an onus on editorial staff to ensure
-that content will be found when a suggested query is used. It might
-serve the website users better to find mechanisms by which to generate
-a useful set of suggestions from the corpus of content as it is
-indexed. The heterogenous nature of BBC content turns this into
-further integration work where different business rules are likely required
-to generate suggestions from different types of content.
-
 In chapter~\ref{stateoftheart} I will briefly outline some of the state of the

### 2014-05-06 chapter3.tex
Added more to chapter 3
Slow progress with chapter3 and moved some stuff from chapter 1 as that's still too long.

--- 2014-05-05 chapter3.tex
@@
 \subsection{The Content}
+\label{content}
 
 The front end search application currently divides all the searchable
-content into so-called ``zones'',
+content into so-called ``zones''. Table~\ref{zones-table}
+
+%TODO - is this all of them?
+\begin{table}[h]
+\begin{tabular}{| l | l |}
+  Zone/Category          & Notes/Comments \\
+  \hline
+  About the BBC          &  Static pages, blogs, articles. RSS/Atom feeds available. \\
+  Blogs                  &  Legacy blog content. RSS/Atom available. \\
+  CBBC                   &  Pages, games, programmes information for Children. Some semantic markup exists for Facebook's Open Graph. \\
+  Films                  &  Legacy site for BBC Film Network and current site for BBC Films. Little semantic markup. \\
+  Food                   &  Recipes features on BBC programmes. No semantic markup despite sister website BBC Good Food website using Schema.org microdata. \\
+  Gardening              &  Legacy website not updated since 2006. All static HTML content with no semantic markup. \\
+  Health \& Parenting    &  \\
+  History                &  \\
+  iPlayer                &  \\
+  Learning               &  \\
+  Local (archive)        &  \\
+  Music                  &  \\
+  News                   &  \\
+  Ouch!                  &  \\
+  Religion \& Ethics     &  \\
+  Science \& Nature      &  \\
+  Sport                  &  \\
+  Teenagers              &  \\
+  TV \& Radio Programmes &  \\
+  TV \& Radio Sites      &  \\
+\end{tabular}
+\caption{Categories or ``zones'' of content currently indexed by BBC Search.}
+\label{zones-table}
+\end{table}
+
+Some of these zones or categories are related to major, well-known areas of
+BBC online. Some seem to be more esoteric or legacy areas, many of which
+are obtained through a web crawler. The presence of ``iPlayer'',
+``TV \& Radio Programmes'' and ``TV \& Radio Sites'' is a distinction that
+has arisen for technical and historic reasons, which is not likely to be
+clear to users.
+
+There is a wealth of legacy content that is likely to be obtainable only by
+crawling. Some active sites are syndicated via RSS/Atom, but a subscription-based
+feed does not allow indexing a backfill of content easily.
 
@@
 
+The default results page currently returned for a query breaks the individual
+results into the zones or categories mentioned in section~\ref{content}. A
+navigation menu on the left allows users to drill down into the results just
+for that category.
+
 \section{Editor's Choice}
 
+Each and every link promoted within this feature is hand-chosen by editorial
+staff and much manual effort is needed to keep promoting new concepts
+as they appear and to remove pages as they get superseded. It is hoped
+in this proposal we can reduce some of that manual curation through the use
+of linked data and demonstrate ways editorial staff can focus on curating
+their own linked data such that Editor's Choice could evolve into a more
+generalised and automated subsystem. A metadata-driven curation system
+could use common patterns in the data to promote orders of magnitude more
+top links with a fraction of the current effort.
+
 \section{Search Suggest}
+
+The list of suggestions that might surface in this system are
+currently chosen and maintained by hand by editorial staff. If a new
+concept breaks into the news (such as a notable person becoming notable
+for the first time), then a person must enter that term into the system.
+Similarly, if something should not be suggested to users any longer
+(perhaps for legal reasons or simply because it is no longer a relevant
+concept), then it must be amended or removed manually.
+
+This manual maintenance of the suggestion list also leads to a
+disconnect between searchable content and suggested queries that might
+appear as users type. There is an onus on editorial staff to ensure
+that content will be found when a suggested query is used. It might
+serve the website users better to find mechanisms by which to generate
+a useful set of suggestions from the corpus of content as it is
+indexed. The heterogenous nature of BBC content turns this into
+further integration work where different business rules are likely required
+to generate suggestions from different types of content.

### 2014-05-09 chapter3.1.tex
Made diagram of Question Time.

--- 2014-05-05 chapter3.tex
@@
-\chapter{Analysis}
-
-In this chapter, I will give a deeper analysis of the four
-components of the search application identified in
-chapter~\ref{intro} and start to highlight areas where linked data
-approaches or semantic web technologies could have a r\^ole to play.
-
 \section{Indexing Content}
@@
 \subsection{The Content}
+\label{content}
 
 The front end search application currently divides all the searchable
-content into so-called ``zones'',
+content into so-called ``zones''. Table~\ref{zones-table}
 
-\section{Search Results Page}
+%TODO - is this all of them?
+\begin{table}[h]
+\begin{tabular}{| l | l |}
+  Zone/Category          & Notes/Comments \\
+  \hline
+  About the BBC          &  Static pages, blogs, articles. RSS/Atom feeds available. \\
+  Blogs                  &  Legacy blog content. RSS/Atom available. \\
+  CBBC                   &  Pages, games, programmes information for Children. Some semantic markup exists for Facebook's Open Graph. \\
+  Films                  &  Legacy site for BBC Film Network and current site for BBC Films. Little semantic markup. \\
+  Food                   &  Recipes features on BBC programmes. No semantic markup despite sister website BBC Good Food website using Schema.org microdata. \\
+  Gardening              &  Legacy website not updated since 2006. All static HTML content with no semantic markup. \\
+  Health \& Parenting    &  \\
+  History                &  \\
+  iPlayer                &  \\
+  Learning               &  \\
+  Local (archive)        &  \\
+  Music                  &  \\
+  News                   &  \\
+  Ouch!                  &  \\
+  Religion \& Ethics     &  \\
+  Science \& Nature      &  \\
+  Sport                  &  \\
+  Teenagers              &  \\
+  TV \& Radio Programmes &  \\
+  TV \& Radio Sites      &  \\
+\end{tabular}
+\caption{Categories or ``zones'' of content currently indexed by BBC Search.}
+\label{zones-table}
+\end{table}
 
-\section{Editor's Choice}
+Some of these zones or categories are related to major, well-known areas of
+BBC online. Some seem to be more esoteric or legacy areas, many of which
+are obtained through a web crawler. The presence of ``iPlayer'',
+``TV \& Radio Programmes'' and ``TV \& Radio Sites'' is a distinction that
+has arisen for technical and historic reasons, which is not likely to be
+clear to users.
 
-\section{Search Suggest}
+There is a wealth of legacy content that is likely to be obtainable only by
+crawling. Some active sites are syndicated via RSS/Atom, but a subscription-based
+feed does not allow indexing a backfill of content easily.
+
+\subsection{Programmes}
+
+Figure~\ref{question-time} depicts semantic metadata found within the home page
+of the \emph{Question Time} microsite.
+
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{question-time.png}
+  \end{center}
+  \caption{Semantic metadata found within \emph{Question Time} home page}
+  \label{question-time}
+\end{sidewaysfigure}

### 2014-05-09 chapter3.tex
Made diagram of Question Time.

@@
 
-\section{Indexing Content}
-
-\subsection{Overview}
-
-The Search application needs to read in or receive metadata about
-BBC content from a variety of sources and then needs to serve
-a diverse set of use cases.\cite{fenning2014applicability} The
-need to integrate against different data sources and funnel
-that information into a common set of search indexes can
-typically be seen as an enterprise integration
-problem.
-
-Some of the data are fairly flat, textual content such as articles and some
-information -- such as programmes -- is very structured (e.g. programmes,
-series, episodes, times of broadcast, channel on which they are broadcast,
-what times they are available to watch on iPlayer, what kinds of devices
-are permitted by rights to watch them on iPlayer). There are challenges
-in providing a consistent and meaningful user experience across such
-a heterogeneous mix of content.
-
-We can achieve some uniformity of the data by building a single, common
-API through which all content is fed into the Search application. However,
-some integration work needs to be
-done by either the owners of the content to send content to the API
-or the developers of the Search application, who can integrate
-existing feeds via an adapter pattern.
-
-Some pages on the BBC website no
-longer have a dedicated team maintaining them and can sometimes only
-be discovered via a web crawl as an external search engine would do. A lot
-of metadata about content also lives in a diverse range of databases and
-content management systems, which may or may not be easily retrievable
-via the public web.
-
-\subsection{Current Implementation}
-
-\begin{dot2tex}[dot,options=-tmath]
-digraph ingest {
-  rankdir=LR;
-
-  Programmes -> Dynamite
-  Dynamite -> FileBasedQueues
-
-  News -> CPS
-  Newsround -> CPS
-  Newsbeat -> CPS
-  Sport -> CPS  
-  CPS -> FileBasedQueues
-
-  MarketData -> FileBasedQueues
-
-  trans3 [label="Transformation"]
-  WorldService -> trans3
-  trans3 -> IngestAPI
-
-  ProgrammesWebsites -> Crawler
-  BBCFood -> Crawler
-  LegacyWebsites -> Crawler
-  trans2 [label="Transformation"]
-  Crawler -> trans2
-  trans2 -> IngestAPI
-
-  IngestAPI -> SearchIndexes
-
-  FileBasedQueues -> Transformation
-  Transformation -> SearchIndexes
-}
-\end{dot2tex}
-
-Figure 1 shows an informal view of the flow of information into the
-search indexes. Note that some content is transformed
-by integration applications written by the Search team whilst some
-is pushed via a so-called ``Ingest API''. This API ensures that
-all content is normalised to some common format and vocabulary before
-it is sent to the indexes. From the perspective of the search application
-system, this reduces the complexity of having to map multiple formats
-and vocabularies to the common representation.
-
-However, if we consider the holistic BBC online system, that transformation
-and integration work still needs to happen. It is arguably more efficient to
-push the integration efforts back onto the respective teams and domain experts
-in charge of each type of content, but that then puts burden on those teams
-to prioritise integrating with the search system over other work planned
-for their product. This is especially difficult again for content that no
-longer has a team actively maintaining it, which is shown by the need
-to transform all content found via the Crawler; there is no clear team to
-whom the transformation/integration could be delegated.
-
-It is clear that the search application has the need to normalise vocabularies
-to some extend (e.g. is it ``title'', ``headline'' or ``display title''
-that I should display as the link text on the results page?) and this requires
-some form of transformation. This frames the search application as being a
-key system whose primary r\^ole is to break down all the content silos in the
-BBC, which was noted as a motivation for Linked Data in chapter 2.
-
-There is also an apparent requirement that we are cautious of delegating
-too much integration work to other teams. From the perspective of teams
-whose products produce content, the ideal search system would be
-``light touch'' and reasonably passive at indexing their content. This
-expectation is strengthened by the long history of public, general-purpose
-web search engines such as Google who seem to find websites by themselves
-and index them without any input from webmasters. However, it should
-not be overlooked that Google does in fact place some burden on webmasters
-to increase the crawlability and indexability of their websites. This
-burden is welcomed due to the benefits of higher rankings that emerge
-after sinking those costs.
-
-Can the same be said that a particular web team
-in the BBC would welcome additional integration effort for the search system?
-Are there benefits that would justify their integration costs? Perhaps if
-these teams have already sunk the costs of optimising their content for
-Google, the search system can at least make use of these efforts and only
-require additional integration work if there are further benefits?
-
-\subsection{The Content}
-\label{content}
-
-The front end search application currently divides all the searchable
-content into so-called ``zones''. Table~\ref{zones-table}
-
-%TODO - is this all of them?
-\begin{table}[h]
-\begin{tabular}{| l | l |}
-  Zone/Category          & Notes/Comments \\
-  \hline
-  About the BBC          &  Static pages, blogs, articles. RSS/Atom feeds available. \\
-  Blogs                  &  Legacy blog content. RSS/Atom available. \\
-  CBBC                   &  Pages, games, programmes information for Children. Some semantic markup exists for Facebook's Open Graph. \\
-  Films                  &  Legacy site for BBC Film Network and current site for BBC Films. Little semantic markup. \\
-  Food                   &  Recipes features on BBC programmes. No semantic markup despite sister website BBC Good Food website using Schema.org microdata. \\
-  Gardening              &  Legacy website not updated since 2006. All static HTML content with no semantic markup. \\
-  Health \& Parenting    &  \\
-  History                &  \\
-  iPlayer                &  \\
-  Learning               &  \\
-  Local (archive)        &  \\
-  Music                  &  \\
-  News                   &  \\
-  Ouch!                  &  \\
-  Religion \& Ethics     &  \\
-  Science \& Nature      &  \\
-  Sport                  &  \\
-  Teenagers              &  \\
-  TV \& Radio Programmes &  \\
-  TV \& Radio Sites      &  \\
-\end{tabular}
-\caption{Categories or ``zones'' of content currently indexed by BBC Search.}
-\label{zones-table}
-\end{table}
-
-Some of these zones or categories are related to major, well-known areas of
-BBC online. Some seem to be more esoteric or legacy areas, many of which
-are obtained through a web crawler. The presence of ``iPlayer'',
-``TV \& Radio Programmes'' and ``TV \& Radio Sites'' is a distinction that
-has arisen for technical and historic reasons, which is not likely to be
-clear to users.
-
-There is a wealth of legacy content that is likely to be obtainable only by
-crawling. Some active sites are syndicated via RSS/Atom, but a subscription-based
-feed does not allow indexing a backfill of content easily.
+\input{chapter3.1}
 
@@
 top links with a fraction of the current effort.
+However, there would be a need to get a list of the known static pages
+as they will not appear in the RSS/Atom feeds. Some integration with the
+underlying CMS may be necessary or we would have to rely on web crawling
+to find these pages.
 

### 2014-05-09 url2rdf.py

@@ -1,0 +1,24 @@
+import sys
+import rdflib
+from rdflib.tools.rdf2dot import rdf2dot
+
+g = rdflib.Graph()
+for url in sys.argv[1:]:
+    g.parse(url)
+
+    if 'http://www.bbc.co.uk/programmes/' in url and '.rdf' not in url:
+        g.parse(url + '.rdf')
+
+    for subject in g.subjects():
+        if 'http://www.bbc.co.uk/programmes/' in subject and '.rdf' not in subject:
+            g.add((rdflib.URIRef(subject), rdflib.URIRef('http://xmlns.com/foaf/0.1/primaryTopic'), rdflib.URIRef(subject + '#programme')))
+
+g.bind('bbcprog', 'http://www.bbc.co.uk/programmes/')
+
+[g.remove((s, p, o))
+ for s, p, o in g
+ if p == rdflib.URIRef(u'http://www.w3.org/1999/xhtml/vocab#role') or o == rdflib.URIRef('http://www.w3.org/1999/02/22-rdf-syntax-ns#nil') ]
+
+#print g.serialize(format='turtle')
+
+print rdf2dot(g, sys.stdout)

### 2014-05-11 chapter3.1.tex
Substantial work on chapter 4. Committing so I don't lose anything.

@@
 
-\begin{dot2tex}[dot,options=-tmath]
+\begin{sidewaysfigure}
+  \begin{center}
+\begin{dot2tex}[dot,scale=0.6]
 digraph ingest {
-  rankdir=LR;
+  rankdir=TB;
+
+  Programmes [shape=rect]
+  News [shape=rect]
+  Newsround [shape=rect]
+  Newsbeat [shape=rect]
+  Sport [shape=rect]
+  MarketData [shape=rect]
+  WorldService [shape=rect]
+  BBCFood [shape=rect]
+  ProgrammesWebsites [shape=rect]
+  LegacyWebsites [shape=rect]
+
+  SearchIndexes [shape=circle]
 
@@
 \end{dot2tex}
+  \end{center}
+  \caption{Abstract model of indexing process}
+  \label{indexing-chain}
+\end{sidewaysfigure}
 
@@
 It is clear that the search application has the need to normalise vocabularies
-to some extend (e.g. is it ``title'', ``headline'' or ``display title''
+to some extent (e.g. is it ``title'', ``headline'' or ``display title''
 that I should display as the link text on the results page?) and this requires
@@
 %TODO - is this all of them?
-\begin{table}[h]
-\begin{tabular}{| l | l |}
+\begin{sidewaysfigure}
+  \centering
+\begin{tabular}{| p{5cm} | p{16cm} |}
+  \hline
   Zone/Category          & Notes/Comments \\
@@
   About the BBC          &  Static pages, blogs, articles. RSS/Atom feeds available. \\
+  \hline
   Blogs                  &  Legacy blog content. RSS/Atom available. \\
+  \hline
   CBBC                   &  Pages, games, programmes information for Children. Some semantic markup exists for Facebook's Open Graph. \\
+  \hline
   Films                  &  Legacy site for BBC Film Network and current site for BBC Films. Little semantic markup. \\
+  \hline
   Food                   &  Recipes features on BBC programmes. No semantic markup despite sister website BBC Good Food website using Schema.org microdata. \\
+  \hline
   Gardening              &  Legacy website not updated since 2006. All static HTML content with no semantic markup. \\
+  \hline
   Health \& Parenting    &  \\
+  \hline
   History                &  \\
+  \hline
   iPlayer                &  \\
+  \hline
   Learning               &  \\
+  \hline
   Local (archive)        &  \\
+  \hline
   Music                  &  \\
+  \hline
   News                   &  \\
+  \hline
   Ouch!                  &  \\
+  \hline
   Religion \& Ethics     &  \\
+  \hline
   Science \& Nature      &  \\
+  \hline
   Sport                  &  \\
+  \hline
   Teenagers              &  \\
+  \hline
   TV \& Radio Programmes &  \\
+  \hline
   TV \& Radio Sites      &  \\
+  \hline
 \end{tabular}
@@
 \label{zones-table}
-\end{table}
+\end{sidewaysfigure}
 
@@
 \subsection{Programmes}
+\label{programmes}
 
 Figure~\ref{question-time} depicts semantic metadata found within the home page
-of the \emph{Question Time} microsite.
+of the \emph{Question Time} microsite. The CURIE\cite{birbeck2009curie}
+\texttt{bbcprog:b043b2rs} (the prefix \texttt{bbcprog} is used here in place
+of \texttt{http://www.bbc.co.uk/programmes/} for convenience)
+describes the page itself as visited in the
+browser. This home page for Question Time is a destination the search
+application might send a user who has indicated in their query that it
+is likely a page they are looking to find, e.g. if they had simply
+searched for ``question time''.
+
+In this case, this graph of metadata has come not just from microdata
+in the home page, but also by merging it with the alternative RDF/XML
+representation that appears to contain more detailed information.
+It was necessary to have some knowledge of this behaviour of the
+programmes microsites -- that they have multiple representations
+in different media types -- since the microdata in the HTML view
+does not link to the RDF/XML view in any way. Such small bits of
+knowledge and business rules about the BBC's own online content
+is a way a BBC-specific search product can gather information publically-available
+as linked data, but in a more considered way and have advantages over
+public search engines such as Google and Bing.
 
@@
 \end{sidewaysfigure}
+
+Note the distinction between the identifier for the microsite's
+\emph{page} and the identifier for concept of \emph{Question Time}
+itself. For the latter, the URI
+\texttt{https://www.bbc.co.uk/programmes/b043b2rs\#programme}
+is used.\cite{raimond2010use}
+
+This abstract entity is classified as a \emph{Brand} in the
+Programmes Ontology\cite{raimond2009bbc} (\texttt{po:Brand})
+developed by Raimond et al. in 2009. This and other concepts
+from the Programmes Ontology were also adopted into the
+Schema.org vocabulary in 2013.\cite{raimond2013schema}
+Figure~\ref{question-time} also shows
+that Question Time is thus classified as a \emph{Series}
+(\texttt{schema:Series}). This could cause confusion given
+that there is a Series class also within the Programmes Ontology,
+whose equivalent in Schema.org is a \emph{Season}. This emphasises
+the importance of firmly understanding what vocabulary is in use
+when integrated with a system and having consistent, considered
+mappings between vocabularies where needed.
+
+The Question Time brand has associated metadata that might
+be useful for a search application to display or index. A title
+suitable for displaying is given along with synopses of two
+different lengths, which might form part of a snippet. We are also
+told that the programme falls within \emph{genres} indentified
+by \texttt{bbcprog:genres/factual/politics\#genre} and
+\texttt{bbcprog:genres/news\#genre}. This URI pattern is
+clear enough to a human reader to represent a \emph{Politics}
+subgenre (underneath a \emph{Factual} genre) and a
+\emph{News} genre respectively. However, if we wish to make
+use of this in any applications, the correct approach with
+linked data is to dereference those identifiers to find
+metadata we can display or index.
+
+Following the politics subgenre URL, we can produce the
+semantic representation shown in figure~\ref{politics}.
+An indexing process that follows certain linked entities
+could, for example, index the Question Time home page
+against the keywords ``politics'' or index a film's
+page against the names of actors that appear therein.
+Linked concepts might also drive decorations and controls
+on the search results pages themselves or the search
+application might even be able to provide faceting, filtering
+and aggregation across content that shares common properties.
+
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{politics.png}
+  \end{center}
+  \caption{Semantic metadata around the \emph{Politics} programme genre}
+  \label{politics}
+\end{sidewaysfigure}
+
+Returning to the semantic view of Question Time in figure~\ref{question-time},
+we can see that the page also describes further entities representing
+a \emph{episodes} with identifiers \texttt{bbcprog:b006t1q9\#programme}
+and \texttt{bbcprog:b04446v3\#programmes}. There are a far greater
+number of episodes linked, but the illustration here is reduced to
+just the two for brevity.
+
+One of the episodes has links to its own page and information
+about how to watch that episode. The graph in figure~\ref{question-time}
+depicts the most recent episode at the time of writing and the
+semantic data given tells us quite a lot about it. We can see
+that there is a linked video (representing as blank node of
+class \texttt{schema:VideoObject}), named ``BBC iPlayer'' with
+a URL (\texttt{schema:url}) of \texttt{http://www.bbc.co.uk/iplayer/episode/b043b2rs}.
+This tells us that we can currently follow that URL to watch
+this episode on BBC iPlayer, which is an example of a useful
+call-to-action that might be placed a search results page where
+a programme is one of the results returned.
+
+We can also see that the time interval in which this is available
+to watch (\texttt{schema:OnDemandEvent}) ends on 8 May, 2015. A
+search application might make use of this to prefer or perhaps
+only show results for programmes that are within this availability
+window. This is the current behaviour for search feature within
+the iPlayer website, but all the availability information is
+obtained via direct integration with service APIs.
+
+The time and date of the next broadcast of this episode is also shown.
+From the graph depicted, we can see there is a (presumably repeat)
+broadcast to occur on Sunday, 11 May 2014 on the BBC Parliament
+channel. Again, this is information that can be displayed within
+search results that might well answer some queries directly
+such as ``When it Question Time next on TV?''. This is similar
+to functionality offered by Google where currency conversions,
+flight times and other quick answers are displayed at the top
+of the results for any query it deems has a straight answer.
+
+Finally, note there is some metadata about the pages themselves
+that are repeated within the Open Graph protocol namespace
+(prefixed with \texttt{og:}). It is common for BBC pages (and
+in fact pages on the web in general) to have embedded Open
+Graph metadata to integrate into Facebook's social graph, even
+when no other semantic markup or metadata are present. Whilst
+the original intention was for Facebook integration, linked
+data technologies will allow us to derive information from
+these properties beyond their intended purpose.
+
+Overall, there are a lot of metadata obtainable about BBC
+programmes via semantic markup available on the public web. There is
+still some information that we cannot obtain:
+
+\begin{itemize}
+  \item We cannot easily gather a list of all identifiers that might
+    be interesting to the search application. Crawling links is
+    popular with web crawlers, but there is no guarantee of finding
+    everything and there are difficulties knowing when to get an
+    updated version of a page when it changes. A BBC-specific
+    search can and arguably should make use of internal integration
+    to discover and update programmes information as it is created,
+    changed or removed.
+  \item BBC iPlayer can display the names of contributors to a programme
+    such as the producers, directors, actors, etc. This information
+    does not appear to be present in the semantic metadata within
+    the programmes microsites.
+  \item Linked Data follows an \emph{Open World} assumption,
+    which means that the lack of fact being asserted does not imply
+    that fact is not true. In our Question Time example above, the
+    fact that Question Time is not asserted to be a comedy does not
+    strictly imply that it is not a comedy.
+\end{itemize}
+
+The open world assumption is not always problematic
+if we are positively adding
+decoration, calls-to-action, query matching, etc. based on
+facts we do have and just allow things to be missing when
+the data are insufficient. Problems are introduced, however,
+if we start to make assumptions, for example, that the
+OnDemandEvent time interval being in the past means the
+programme is definitely not available to watch in iPlayer.
+
+In this example, missing off the link to iPlayer might merely
+inconvenience a user who has to click around a bit more to
+find the iPlayer link. If, however, the search application
+chose not to respond with the programme at all under the
+impression it is not available to watch, then there is an
+arguably more broken user experience.
+
+In some situations it may be preferable to integrate against
+a service or data source to get a definitive and \emph{complete}
+answer, i.e. one with which we can make closed world assumptions.
+In other words, if the data source does not tell us a programme
+is available right now to watch on BBC iPlayer, then we can
+strictly and validly infer that it is not available to watch.
+
+The trade-offs between open and closed world assumptions need to
+be kept in mind for any information architecture around the
+search results pages and for any domain modelling for the
+search indexes. Care should be taken around any design element
+or feature that is affected the lack of information. Ideally,
+all behaviour would follow a \emph{progressive enhancement} model
+where additional information can only improve the system's
+behaviour
+and the omission of details or data leads to a \emph{degraded}
+rather than \emph{broken} experience.
+
+The programmes dataset is normally the most structured and
+complex to work with, but is one of the leading uses of
+semantic web technologies on the BBC website as a whole. In
+the rest of this sectio, I will briefly touch on any different
+challenges from other datasets.
+
+\subsection{News}
+
+The semantic metadata that can be found in a BBC News article
+page is notably less complex that a programmes microsite, as
+can be seen in figure~\ref{keepod}.
+
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{keepod.png}
+  \end{center}
+  \caption{Metadata found within a BBC News article page}
+  \label{keepod}
+\end{sidewaysfigure}
+
+As discusseed in section~\ref{programmes}, BBC News also makes
+use of Facebook's Open Graph metadata and a search application
+could derive information about this article from those properties.
+
+There is also a second vocabulary in use, namely rNews -- an RDFa
+vocabulary developed by the International Press Telecommunications Council
+(IPTC) to annotate online news content.
+
+Note that \texttt{rnews:headline} and \texttt{og:title} agree on
+the title/headline for the article, but \texttt{og:image} and
+\texttt{rnews:thumbnailUrl} point to two different URLs for
+an image to accompany the article. In this case, \texttt{og:image}
+just points to a BBC News logo image and \texttt{rnews:thumbnailUrl}
+shows an image related to the article, albeit only 66 pixels wide
+by 49 pixels high.
+
+So, if we wish to create a search application that shows thumbnails next
+to results, which image is better to use? Can we create general-case
+rules that apply more ``trust'' to one image property over another?
+
+Also, a larger problem is that a semantic extraction on this page
+has not actually given us the article's text content in any way. The
+current BBC Search application uses all text within an article as
+potential keywords so that a user can search for phrases that appear
+anywhere within an article in theory. If we are to extract that text
+for indexing, we encounter all the usual pitfalls of non-semantic
+web crawling and indexing -- e.g. it is not always clear where
+in the HTML the article's ``body'' is (we might accidentally index
+things like the navigation menu) and the crawler needs updating
+if the HTML layout of the page changes.
+
+One significant gap in the semantic markup of BBC News articles is
+the lack of relating the content of the articles to notable entities.
+For instance, any mention of people or places could be captured
+to provide aggregations across those concepts or at least make it
+easier to find an article by typing the names of concepts and things
+mentioned therein.
+
+Annotations of concepts in an article is best done by journalists
+and editors, but can we automate some of the process, at least
+to suggest annotations to use? One approach is to make use of
+DBPedia Spotlight to extract concepts that may be mentioned in
+an article.
+
+\begin{sidewaysfigure}
+  \begin{center}
+    \includegraphics[width=\linewidth]{keepod-tagged.png}
+  \end{center}
+  \caption{BBC News article page's metadata enriched using DBPedia Spotlight}
+  \label{keepod-tagged}
+\end{sidewaysfigure}
+
+A na\"ive first-pass use of DBPedia Spotlight could enrich
+our article's semantic graph to that depicted in figure~\ref{keepod-tagged}.
+Arbitrary values of 10 and 0.25 were used for the \emph{support}
+and \emph{confidence} parameters respectively. These values were
+chosen based on the their returning a small handful of tags, but
+a more considered approach might dynamically adjust these values
+optimised for desired behaviour of the search application.
+
+Automatic tagging with systems such as DBPedia Spotlight is a good
+example of an approach that \emph{can} be taken to enrich
+the metadata, but it is not clear from the analysis so far as to
+whether the search application \emph{should} enrich in this way
+nor what benefits it brings.
+
+One remaining piece of information that is still lacking is
+what News category in which the article falls. The BBC News
+website has business rules around categorising all news
+content -- e.g. \emph{Technology}, \emph{Scotland}, \emph{Education}
+-- but this categorisation seems lacking from the semantic markup. The
+current BBC Search application decorates all news results with
+their respective news category, so an indexing chain using
+the linked data within the news pages alone would need need
+to enrich with that information.
+
+It should not be forgotten that BBC News content dates back to the
+1990s and semantic metadata that can be extracted is going
+to vary greatly in quality. The search application is sometimes
+the only way to navigate to such historic content and any indexing
+work needs to be accepting of this variation over the years.
+
+\subsection{Sport}
+
+%TODO - Finish this

### 2014-05-11 chapter4.1.tex
Substantial work on chapter 4. Committing so I don't lose anything.

\section{Linked Data Indexing}

The concept of \emph{Linked Enterprise Data} was introduced and described
in section~\ref{linked-enterprise-data}. In this section, it is proposed
to endeavour to make use of this approach where possible in the
ingest and indexing processes of the BBC Search application.

\begin{figure}
  \begin{center}
\begin{dot2tex}[dot,scale=0.55]
digraph ingest {
  rankdir=TB;

  Programmes [shape=rect,label=iPlayer]
  News [shape=rect]
  Newsround [shape=rect]
  Newsbeat [shape=rect]
  Sport [shape=rect]
  MarketData [shape=rect]
  WorldService [shape=rect]
  BBCFood [shape=rect]
  ProgrammesWebsites [shape=rect,label=Programmes]
  LegacyWebsites [shape=rect,label="Legacy Sites"]

  SearchIndexes [shape=circle]

  Programmes -> URLNotification [label="URLs"]

  News -> CPS
  Newsround -> CPS
  Newsbeat -> CPS
  Sport -> CPS

  CPS -> URLNotification [label="URLs"]

  URLFetch -> "www.bbc.co.uk" [label="HTTP\ GET"]
  "www.bbc.co.uk" -> URLFetch [label="RDFa/Microdata"]

  trans3 [label="Transformation"]
  WorldService -> trans3
  MarketData -> trans3
  trans3 -> IngestAPI [label="Atom"]

  ProgrammesWebsites -> Crawler
  BBCFood -> Crawler
  LegacyWebsites -> Crawler

  Crawler -> URLNotification [label="URLs"]

  URLNotification -> URLFetch [label="RDF"]

  URLFetch -> Enrichment [label="RDF"]
  URLFetch -> Inference [label="RDF"]

  Enrichment -> Inference [label="RDF"]

  Inference -> IngestAPI [label="RDF"]

  IngestAPI -> SearchIndexes

}
\end{dot2tex}
  \end{center}
  \caption{Abstract model of proposed indexing process}
  \label{led-indexing-chain}
\end{figure}

An abstract overview of the flow of content is given in figure~\ref{led-indexing-chain}.
As with the current system depicted in figure~\ref{indexing-chain},
there remains an ``Ingest'' API to which any system may
send content to be indexed if it has already been transformed to
use the semantics required by the search application. This
ensures that integration work done by other teams continues to work
and retains the use case where content producers wish to have full
control of what metadata is sent to the search indexed -- as long as
they are willing to do the integration work.

Bespoke integration in this way can still suffer from maintainability
problems that occur when systems are too tightly coupled. Due to this,
it is architecturally important that the Ingest API continues to follow
the REST architectural style, making appropriate use of Hypermedia to
evolve the API's semantics over time whilst not breaking existing clients.

Where this proposal differs from the existing approach is in the case
of more ``light touch'' integration for teams who are less able or willing
to do bespoke transformation work and increasing coupling to the search
APIs. The goal of this part of the proposal is to reduce the integration
and consequent maintenance work for the search development team.

For these cases, the indexing chain starts from the \emph{URLNotification}
stage to which messages can be sent in
\texttt{text/uri-list}\cite{amundsen2011hypermedia} format. It is expected
that there is some mechanism by which this service can be notified with URLs
of every piece of content that has been created or updated on the BBC website.
This might take the form of the search team's own crawler that is seeking
out pages that have not been found yet or it could be a message-driven
notification process. It is hoped that whilst it might be demanding to
put the onus on a team
to provide transformed content and to integrate against the search system's
APIs, it is a far lighter piece of work to send simple notifications containing
a URL.

The URLNotification service can generate a minimal RDF graph and the
rest of the indexing chain can be seen as a process that incrementally
augments this graph until it is suitable for indexing and has sufficient
information to display search results. It is proposed that these minimal
graphs will take the form of the following example (in JSON-LD serialisation):

\begin{centering}
\begin{lstlisting}[language=json]
[
  {
    "@id": "http://www.bbc.co.uk/news/technology-27346567",
    "http://purl.org/dc/terms/identifier": [
      {
        "@value": "http://www.bbc.co.uk/news/technology-27346567"
      }
    ]
  }
]
\end{lstlisting}
\end{centering}

This single triple, whilst arguably tautological, can serve as a stub
for the series of augmentations further downstream. The next stage,
the \emph{URLFetch} stage, is
the attempt to add semantic metadata found by dereferencing the URL
given. This step should retrieve metadata similar to the graphs depicted
in chapter~\ref{analysis} such as figure~\ref{keepod}. If the identifier
in the stub RDF graph sent to this stage is a URI, but not a URL, then
dereferencing is not possible, but the \emph{URLFetch} stage could
passively send the graph onwards without augmenting to it.

In the URLFetch stage, it might be necessary to apply some web scraping/crawling
techniques to extract the body of text from articles where appropriate.
It was identified in the case of figure~\ref{keepod} that BBC News
was not semantically highlighting the actual text content of the articles, but
a search application is certainly interested in this information.

The URLFetch service can then send the augmented graph onwards to
the \emph{Enrichment} service. The purpose of this stage is to apply
any number of business rules to add further metadata to the graph
that has not been obtainable via the public website or further upstream. It is
in this service that the search team is doing more classical
\emph{enterprise integration} work, which is unavoidable, but confined
to this one service (or collection of microservices).

In the Enrichment service, we might, for example, contact backend
service applications for futher data about the content we are trying to ingest.
This might mean fetching information about a programme from services
behind BBC iPlayer or contacting content management systems for
non-published metadata about articles, videos, etc.

Depending on the nature of the data source, this might allow us to start
making \emph{closed world} assumptions about the properties of content
items. In section~\ref{programmes}, it was noted that the \emph{open world}
assumption of linked data would make it difficult to assert negative
things about the content (e.g. this programme is not available to
watch on iPlayer). If we know that our RDF graph has been enriched
with a totality of information \emph{from source}, then it might be
possible to start making some closed world assumptions with certain predicates.

Following the same pattern as the URLFetch stage, it is valid behaviour
for the Enrichment service to assess that it is unable to provide
any useful, additional metadata and to pass the RDF graph further
downstream untouched. This allows an iterative approach where the first
version of the service can only enrich from one data source and
further data sources are added over time. Content items that cannot be
enriched at the present time can simply pass through unchanged.

The next stage is to run the RDF graph through an \emph{Inference} process.
This is where custom rules are invoked to handle the different
vocabularies that might be in use. For example, the rule shown below
(in N3 format) would allow us to infer that we can
use \texttt{schema:headline} anywhere we have used \texttt{rnews:headline}
or \texttt{og:title}.

\begin{centering}
\begin{lstlisting}[language=ttl]
@prefix schema: <http://schema.org/> .
@prefix rnews: <http://iptc.org/std/rNews/2011-10-07#> .
@prefix og: <http://ogp.me/ns#> .

{ ?x rnews:headline ?y } => { ?x schema:headline ?y } .
{ ?x og:title       ?y } => { ?x schema:headline ?y } .
\end{lstlisting}
\end{centering}

This is useful if the decision is made to use the Schema.org vocabulary as
the standard within the search indexes and application, but upstream
content from BBC News is using \texttt{rnews:headline} instead. It is this
mixed used of vocabularies that was a major driver in historic
enterprise integration efforts. In bespoke integration applications, explicit
transformation would be used to translated  ``news item'' to a
``search item'' including the rule that explicitly extracted the
\texttt{rnews:headline} property and set it on the \texttt{schema:headline}
property on the new ``search item'' being created.

In the proposed approach, the RDF model provides a generic framework where
transformation does not need to occur at any syntactic level and we
can use resuable inference rules to make more blanket statements such as
``Where the title has been set for Facebook's Open Graph, use the same
thing for the title on search results''. This rule can then apply to \emph{all}
content that uses that property without regard to what ``kind'' of content item
it is.

This may sound too open to problems where properties are miused in
unexpected ways and that inferring information in key vocabularies from
ones used by other systems might allow for ``dirty data'' to appear. Such
difficulties with the variable quality of linked data on the wider semantic
web were certainly encountered by Hogan et al.\cite{hogan2011searching} when
building the SWSE: the Semantic Web Search Engine. It is argued however,
that these risks are substantially lower for linked enterprise data as
the domain is far more controlled than the public web. It is also an important
feature of the web (both the document web and the semantic web) that linking and
decentralisation bring overall maintainability and interoperability benefits
that outweigh minor integrity concerns that organisations tradtionally attempt
to prevent with strict, controlled vocabularies, governance and bespoke
software integration.

This proposal argues it is more beneficial to take a more agile approach
of validating some minimum requirements of the information before it
enters the search indexes themselves. Any content that is not thus
being accepted can be flagged so that the rules can be amended. For example,
it might be decided that the \texttt{rnews:headline} property is only
correctly used by BBC News and other content producers use it incorrectly. In
this case, we can update our rules as shown below:

\begin{centering}
\begin{lstlisting}[language=ttl]
@prefix schema: <http://schema.org/> .
@prefix rnews: <http://iptc.org/std/rNews/2011-10-07#> .
@prefix og: <http://ogp.me/ns#> .

{ ?x rnews:headline ?y
. ?x og:site_name "BBC News" } => { ?x schema:headline ?y } .
{ ?x og:title             ?y } => { ?x schema:headline ?y } .
\end{lstlisting}
\end{centering}

Here we add an additional constraint
that we only infer the \texttt{schema:headline} property that we might
ultimately use on the search results page from the \texttt{rnews:headline} if
the content has a value for \texttt{og:site\_name} that indicates it came
from BBC News. This can then be iterated on for future rules that define
different behaviour based on different aspects of the content. These inference
rules can be as simple or as complex as needed.

It is even possible to have
completely different sets of rules invoked based on the types of the content
being indexed. Such an approach should be taken with care so as to prevent
being overly brittle and coupled to the exact structure of the content. More
generic rules allow us to add information based on abstract features of the
metadata that might be present across many ``types'' of content.

### 2014-05-11 paper.tex
Drawing a line under chapter 2 for now so I can move on to the important stuff. I've not said anything around inference, but I probably don't need to.
Made some start to chapter 3 and proved getting graphviz working for embedded diagrams.
Made diagram of Question Time.
Substantial work on chapter 4. Committing so I don't lose anything.

@@
 \usepackage{nag}
+
+\usepackage{rotating}
+\usepackage{graphicx}
+
 \usepackage{mathtools}
@@
 \usepackage{url}
+\usepackage{verbatim}
+
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows}
+\usepackage{dot2texi}
+
+\usepackage{listings}
+\usepackage{xcolor}
+
+\colorlet{punct}{red!60!black}
+\definecolor{background}{HTML}{EEEEEE}
+\definecolor{delim}{RGB}{20,105,176}
+\colorlet{numb}{magenta!60!black}
+
+\lstdefinelanguage{json}{
+    basicstyle=\normalfont\ttfamily\footnotesize,
+    numbersep=8pt,
+    showstringspaces=false,
+    breaklines=true,
+    backgroundcolor=\color{background},
+    literate=
+     *{0}{{{\color{numb}0}}}{1}
+      {1}{{{\color{numb}1}}}{1}
+      {2}{{{\color{numb}2}}}{1}
+      {3}{{{\color{numb}3}}}{1}
+      {4}{{{\color{numb}4}}}{1}
+      {5}{{{\color{numb}5}}}{1}
+      {6}{{{\color{numb}6}}}{1}
+      {7}{{{\color{numb}7}}}{1}
+      {8}{{{\color{numb}8}}}{1}
+      {9}{{{\color{numb}9}}}{1}
+      {:}{{{\color{punct}{:}}}}{1}
+      {,}{{{\color{punct}{,}}}}{1}
+      {\{}{{{\color{delim}{\{}}}}{1}
+      {\}}{{{\color{delim}{\}}}}}{1}
+      {[}{{{\color{delim}{[}}}}{1}
+      {]}{{{\color{delim}{]}}}}{1},
+}
+
+% Language Definitions for Turtle
+\definecolor{olivegreen}{rgb}{0.2,0.8,0.5}
+\definecolor{grey}{rgb}{0.5,0.5,0.5}
+\lstdefinelanguage{ttl}{
+    basicstyle=\normalfont\ttfamily\footnotesize,
+    showstringspaces=false,
+sensitive=true,
+morecomment=[l][\color{grey}]{@},
+morecomment=[l][\color{olivegreen}]{\#},
+morestring=[b][\color{blue}]\",
+}
 
@@
 \maketitle
+
+\tableofcontents
 

### 2014-05-11 url2rdf.py

@@ -19,6 +19,6 @@ g.bind('bbcprog', 'http://www.bbc.co.uk/programmes/')
  for s, p, o in g
  if p == rdflib.URIRef(u'http://www.w3.org/1999/xhtml/vocab#role') or o == rdflib.URIRef('http://www.w3.org/1999/02/22-rdf-syntax-ns#nil') ]
 
-#print g.serialize(format='turtle')
+print g.serialize(format='turtle')
 
-print rdf2dot(g, sys.stdout)
+#print rdf2dot(g, sys.stdout)

### 2014-05-12 chapter1.tex
Started chapter 5 and purging mention of suggest as it's turning into scope creep.

@@
 of \emph{Linked Data}\cite{bizer2009linked} and/or the Semantic
-Web\cite{berners2001semantic}. I hope to be able to demonstrate five tangible
+Web\cite{berners2001semantic}. I hope to be able to demonstrate four tangible
 benefits this domain can bring to a search application, namely:
@@
     manner.
-  \item Replacement of the manual curation of autocomplete suggestions
-    in the \emph{Search Suggest} service -- that suggests full text queries
-    as the user types -- with suggestions driven from linked data.
 \end{enumerate}
@@
 
-\section{Search Suggest}
-
-One challenge for the querying of a search application is to be tolerant
-of the variable quality of user-entered queries. Many users of web search
-engines may give ambiguously short queries, overly long queries with (where
-it can be hard for a machine to pick out the important keywords amongst
-less important words or stop words\cite{rajaraman2011data})
-or simply use incorrect spelling.
-
-This problem can be ameliorated with a plethora of algorithm
-server-side solutions (e.g. spell checking), but a simple solution that
-can be implemented on the user interface is an \emph{autocomplete}
-or \emph{autosuggest} feature. The former prompts for potential
-queries, titles, names, etc. that they may be typing so as to prevent
-the need to type the query out in full. The latter feature can go
-further to suggest onwards journeys that bypass the need for a
-page of search results altogether.
-
-The search box for BBC Search implements an autocomplete
-feature -- known
-as \emph{Search Suggest} -- whereby
-the full names or titles of are suggested to users as they type the first
-few characters of their queries. This helps guide users into free text
-queries that are more likely to match terms in the indexes and reduces
-mismatching due to misspellings or otherwise poorly-formed queries.
+\section{Summary}
 

### 2014-05-12 chapter4.1.tex
Started chapter 5 and purging mention of suggest as it's turning into scope creep.

@@
 metadata that might be present across many ``types'' of content.
+
+The final stage after this inference is to push the RDF graph in
+an appropriate hypermedia type such as JSON-LD to the Ingest API. At this
+point, we should have all required fields/properties for indexing as
+well as other properties that came from upstream sources that will not
+immediately be used. It should be the r\^ole of the Ingest API to perform
+some \emph{contextual validation}\cite{fowler2005contextual} to ensure
+it can be indexed. Ones that cannot be indexed should be stored, but
+not indexed, so there is opportunity to retrieve and repush items through
+the Enrichment and Inference stages again if needed.

### 2014-05-12 chapter5.tex
Started chapter 5 and purging mention of suggest as it's turning into scope creep.

\chapter{Implementation Plan}

In the previous chapter, some proposals for improvements to
the search application were outlined, but without any order
of importance, business value nor strategy for implementing them.
In this chapter, I will align these proposals within a road map
that describes how and when these proposals could be implemented
over a twelve month period.

With the view to follow an \emph{Agile} methodology, the use
of \emph{Story Mapping} described by Gigante\cite{gigante2013creating}
is likely to be a more adaptable and managable approach than
trying to plan every detail over a year.

### 2014-05-12 chapter3.2.tex
Some analysis of the results page itself.

\section{Search Results Page}

The majority of the complexity and development arguably lies within
the indexing processes of the search applicatio, but it is with the
\emph{actual Search Engine Results Page} (SERP) that the website users interact.

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{results-page.png}
  \end{center}
  \caption{Results page for BBC Search}
  \label{fig:search-page}
\end{figure}

The different categories/zones are shown on the left menu, with the
number of results found within each category also shown. The first results
are ``Editor's Choice'' results where the application
has matched manually-curated pages against the query. This module appears
as its own distinct category at the top of the list, but functionally
is a distinct feature to the ``organic'' results that follow below.

The organic results are broken into categories such that this ``All Results''
page reached after a search acts as a way to skim over each relevant
category.

The mix of ``iPlayer'' (episodes available to watch on iPlayer),
``TV \& Radio Programmes'' (microsites about programmes, series
and episodes past, present and forthcoming) and ``TV \& Radio Sites''
(web-crawled pages from legacy programme information sites) produces
a bit of redundancy that may confuse users and pushes non-programmes
results below the fold of the page on even desktop screens.

However, fuller analysis of the design and layout of the results page
is a subject for a separate and distinct study. Such an analysis
should certainly be part of the road map for any changes to the
results pages so as to give a broader view of how users interact
with the page and thus what behaviours of the search application
are desirable throughout the entire stack. In this study, the
primary concern is around the appearance and use of metadata
and linkable information.

There is no semantic markup in the results pages, but it might be
questionable as to whether any is needed as the search application
is not \emph{publishing} the data. However, the results page does
make \emph{use} of metadata about content to decorate and alter
the display of each result.

Every search result has the basic trio of title, summary and outgoing
link. Some results (where possible) are accompanied by a thumbnail
image to give more indications about the content they represent. Certain
types of results have a date attached, giving some idea of how recent
the item is. Dates are useful to help users assess the relevance
of results -- a user can dismiss older content if they know they
are looking for new information only.

Some results also carry categorisation specific to their respective
domains. News results are marked with which area of the news
website owns the article (e.g. Politics, Technology, Education). Similarly,
programmes are annotated with which TV or Radio service owns
that programme -- a concept known as the \emph{master brand} of a programme,
e.g. the programme \emph{Doctor Who} is known as a \emph{BBC One} programme.

Video and audio results have call-to-action icons added to indicate
the item can be watched or listened to respectively. These kinds
of annotations are important to give users ideas of how they would
be interacting with the item. This, again, can help a user assess more
accurately if the result is the one for which they are looking.

Currently, whether the item is textual, video or audio is driven by
a metadata field known as \emph{media type}. This classifies the content
into a set of predetermined types and the application uses rules
along the lines of ``if the media type is \emph{video} then add a play icon''.

This works well enough for programmes, but there are areas where
a class-based distinction might not be so clear cut. For example, some articles
on BBC News are accompanied by a video. Is this item textual or a video?
The current search application does not apply a play icon because the
article is classified as textual, as all news story pages are.

### 2014-05-12 chapter4.2.tex
Some analysis of the results page itself.

\section{Search Results Page}

The overall information architecture, design and user experience of
the results page are out of scope for this proposal, but it is likely
there could be some improvements in this area, particulary around making
the web page itself responsive\cite{marcotte2010responsive}. A separate
study might consider reviewing the use cases of BBC Search from
the viewpoint of website visitors and consider the relevant
\emph{search modes} and \emph{mode chains}, which could lead to
an information architecture that would drive metadata requirements.

In this proposal, the focus is to propose what \emph{could} be
achieved in an automated way when the principles of linked data
are introduced to the search application. Ultimately, proposed
changes to the search results page should ideally be supported
by valid analysis from a user experience and information
architecture stance.

### 2014-05-13 chapter3.2.tex
Almost finished chapter 4.

@@
 
-This works well enough for programmes, but there are areas where
+This works well for programmes, but there are areas where
 a class-based distinction might not be so clear cut. For example, some articles
@@
 article is classified as textual, as all news story pages are.
+
+The claim was made that there is limited use in semantically annotating
+this metadata as the search application does not \emph{publish} any data
+that is not already published in its respective area of the BBC website.
+However, given the search system has the primary purpose of bringing
+together content across all the BBC (as noted in section~\ref{sec:current-impl}),
+relationships are established and those relationships are metadata.
+For example, if both a BBC Sport article and a BBC News article mention
+the same entity (say, a footballer who has also appeared in the news),
+the search application is going to put those two items in the same aggregation
+(e.g. search results page) even if just by virtue of keyword matching that
+entity's name in both articles.
+
+There is a feature of the current search application where data or metadata
+are more directly published and that is the ``Editor's Choice'' feature. In
+the next section, the nature of that metadata is explored further.

### 2014-05-13 chapter3.3.tex
Almost finished chapter 4.

\section{Editor's Choice}

Three different categories of search activities were proposed
as part of a model developed by
Gary Marchionini\cite{marchionini2006exploratory}:
\emph{Lookup}, \emph{Learn} and \emph{Investigate}. The
latter two can be grouped under the banner of \emph{exploratory search}
and the diverse spread of organic results on the search results pages
can aid these activities. It is to serve the \emph{Lookup} activity
that the so-called organic results are header with up to three
``Editor's Choice'' links that -- based on the query given -- may
well lead directly to a specific item or location the user was seeking.

Two such distinct modules on the page allow both lookup- and exploration-
style interactions to occur on the same results page. It could be said
that the Google Knowledge Graph\cite{singhal2012introducing} takes
this concept further to provide summaries of entities and links to
specific answers alongside the traditional, keyword-based matches.

The Editor's Choice feature assures that common -- or easily recognisable -- queries
lead to a mix of mechanically-chosen and editorially-curated links,
with the intention this provides a balance between the large-scale
matching of a search engine with some human insight into content
most users are likely to be looking for -- intelligence that is not
so easily bestowed upon a search engine.

Howver, each and every link promoted within this feature is hand-chosen by editorial
staff and much manual effort is needed to keep promoting new concepts
as they appear and to remove pages as they get superseded.

### 2014-05-13 chapter3.tex
Substantial work on chapter 4. Committing so I don't lose anything.
Some analysis of the results page itself.
Almost finished chapter 4.

@@
 \chapter{Analysis}
+\label{analysis}
 
@@
 \input{chapter3.1}
-
-\section{Search Results Page}
-
-The default results page currently returned for a query breaks the individual
-results into the zones or categories mentioned in section~\ref{content}. A
-navigation menu on the left allows users to drill down into the results just
-for that category.
-
-\section{Editor's Choice}
-
-Each and every link promoted within this feature is hand-chosen by editorial
-staff and much manual effort is needed to keep promoting new concepts
-as they appear and to remove pages as they get superseded. It is hoped
-in this proposal we can reduce some of that manual curation through the use
-of linked data and demonstrate ways editorial staff can focus on curating
-their own linked data such that Editor's Choice could evolve into a more
-generalised and automated subsystem. A metadata-driven curation system
-could use common patterns in the data to promote orders of magnitude more
-top links with a fraction of the current effort.
-However, there would be a need to get a list of the known static pages
-as they will not appear in the RSS/Atom feeds. Some integration with the
-underlying CMS may be necessary or we would have to rely on web crawling
-to find these pages.
-
-\section{Search Suggest}
-
-The list of suggestions that might surface in this system are
-currently chosen and maintained by hand by editorial staff. If a new
-concept breaks into the news (such as a notable person becoming notable
-for the first time), then a person must enter that term into the system.
-Similarly, if something should not be suggested to users any longer
-(perhaps for legal reasons or simply because it is no longer a relevant
-concept), then it must be amended or removed manually.
-
-This manual maintenance of the suggestion list also leads to a
-disconnect between searchable content and suggested queries that might
-appear as users type. There is an onus on editorial staff to ensure
-that content will be found when a suggested query is used. It might
-serve the website users better to find mechanisms by which to generate
-a useful set of suggestions from the corpus of content as it is
-indexed. The heterogenous nature of BBC content turns this into
-further integration work where different business rules are likely required
-to generate suggestions from different types of content.
+\input{chapter3.2}
+\input{chapter3.3}

### 2014-05-13 chapter4.2.tex
Almost finished chapter 4.

@@
-\section{Search Results Page}
+\section{Rich Snippets}
 
@@
 architecture stance.
+
+One improvement may be to introduce the rich snippets as described
+in section~\ref{enhancing-results}. The work of Haas et
+al.\cite{haas2011enhanced} included adding the snippets in the presentation
+layer by triggering one of a list of plugins that will alter the
+presentation of the data. The indexing process improvements
+described in section~\ref{sec:ld-indexing} should provide the
+additional structured data to drive a series of rich snippet templates
+for different types of content item.
+
+One drawback with creating a template per ``type'' of item is that a
+developer has to create each template individually and also add templates
+and redeploy the application to add a new type when it emerges.
+The RDF model appears to encourage flexibility through
+\emph{schemaless} data structures, which could limit the ability to
+trigger fixed templates on some types of objects.

### 2014-05-13 chapter4.3.tex
Almost finished chapter 4.

\section{Editor's Choice}

It is proposed there can be
a reduction in some of that manual curation through the use
of linked data and editorial staff can focus on curating
their own linked data. Editor's Choice could evolve into a more
generalised and automated subsystem. A metadata-driven curation system
could use common patterns in the data to promote orders of magnitude more
top links with a fraction of the current effort.

Thus the proposal is to maintain a linked data store in parallel
to the document-oriented search indexes, from which

### 2014-05-14 chapter4.2.tex
Got enough of chapter 4 that I can move on to chapter 5 now.

@@
 
-One drawback with creating a template per ``type'' of item is that a
-developer has to create each template individually and also add templates
-and redeploy the application to add a new type when it emerges.
-The RDF model appears to encourage flexibility through
-\emph{schemaless} data structures, which could limit the ability to
-trigger fixed templates on some types of objects.
+There is a vast number of potential rich details that could be
+incorporated into the search results page, so the initial proposal
+is to pilot a single enhancement and develop further improvements
+through user feedback and testing.

### 2014-05-14 chapter4.3.tex
Got enough of chapter 4 that I can move on to chapter 5 now.

@@
 Thus the proposal is to maintain a linked data store in parallel
-to the document-oriented search indexes, from which
+to the document-oriented search indexes, from which entities
+and concepts themselves can be extracted and indexed to supplement
+the search results centred around web pages.
+
+The names or labels for these entities (as identified by
+predicates such as \texttt{rdfs:label}) can be stored in
+a search index distinct to the index of web pages and this
+will enable the query time searching to perform a dual search
+both for \emph{documents} that contain the given keywords,
+but also \emph{things} that seem to match the same query.
+
+This is superficially similar to the current behaviour in that
+queries that match against concepts in a manually-curated
+taxonomy will return so-called ``best links'' stored
+against those concepts. These links then surface in the 
+``Editor's Choice'' section of the search results page.
+
+However, the accumulation of a single, large graph of
+semantic metadata -- initially as a side effect of
+indexing documents as their own distinct RDF graphs --
+will allow this taxonomy to be grown over time without
+manual intervention.
+
+This does not preclude manual guidance and supervision of the
+concepts that should surface in search results pages. In
+the strictest model, the search system can simply suggest
+entities that appear to be significant (e.g. if more
+than a given number of pages and entities link to it) and an
+editorial admin tool will allow approval of which items are
+notable enough to match against queries. A more relaxed
+model might see some entities with a high number of links
+(for example, if a person or organisation rapidly becomes
+famous in the news and is tagged in multiple news articles
+as a result) being automatically included as potential
+search results.
+
+This follows the principles of linked enterprise data outlined in
+section~\ref{linked-enterprise-data} in that staff within
+an enterprise such as editorial staff in the BBC should be
+creating data in a way that is automatically published. This
+means that bespoke applications where the data are stored in
+a database should be replaced over time with systems that
+simply publish their curation as linked information, perhaps
+directly into the search application's triple store.
+
+Editorial staff might publish assertions such as
+``person $X$ is notable for $Y$'' or
+``programme $X$ is a big name brand for the BBC'' and then
+properties such as \texttt{foaf:homepage}\cite{brickley2012foaf} or
+\texttt{po:microsite}\cite{raimond2009bbc} indicate the canonical
+``home pages'' for those entities. The search application can
+then index all entities that have such editorial interest marked
+against them alongside their home pages and provide an
+Editor's Choice feature that uses the combined strengths
+of automated and manual curation.

### 2014-05-15 chapter5.1.tex
Big push into chapter 5. The road map is outline and just needs filled in really. Then summary and review.

\section{Features}

Whilst most of the proposals in chapter~\ref{ch:proposal} were
technical in nature, most Agile practices encourage phrasing
improvements in terms of changes a user or stakeholder would see
and attach some measure of business value to them. Thus the proposed
improvements around indexing linked data, semantically-driven rich
snippets and semi-automated editorial curation are expressed as
the follow tangible improvments:

\begin{itemize}

\item \textbf{A user can always find the microsite for any programme.}
  This removes the redundancy
  of crawling programmes microsites and indexing iPlayer as separate categories.

\item \textbf{A user has the choice to click through to iPlayer instead of a programme microsite if that programme has episodes available to watch.}
  This turns programmes results into richer
  snippets where a link to iPlayer becomes optional decoration based on whether that information
  is available. If search does not display the link, but it is actually available to watch, the
  programme's microsite will still link to iPlayer, simply adding an extra level of indirection. This
  is arguably preferable to omitting the programme from an ``iPlayer'' category because BBC Search
  (incorrectly) thinks it is not available to watch on demand.

\item \textbf{Search results for programmes should display when that programme is next broadcast.}
  This supports the use case where a user is looking for a ``quick answer'' as to when
  their chosen programme is next broadcast. User testing should contribute to ascertaining how valuable
  this use case is.

\item \textbf{A programme's microsite should always be the top result.}
  In a purely-organic search, it
  is possible that news articles, etc. might contain the same keywords as a programme (e.g. some programm
  titles are incredibly generic, such as \emph{Today} on BBC Radio 4) and those results might conceivably
  be scored more highly. The Editor's Choice feature ensures the programme's microsite is always at
  the top, but with this feature we can migrate the manual curation of these programmes links to
  the proposed, automated system and reduce the need to manually manage this subset of curated links.

\item \textbf{The search results for CBBC and Knowledge and Learning should be improved.}
  These are two BBC sites that are actively maintained, but content is currently obtained by
  the search application via a web crawler. The crawler can be retained for now, but it should
  be sending the content via the new RDF-based indexing chain laid out in section~\ref{sec:ld-indexing}.
  This will give the opportunity to extract some semantic data (CBBC at least uses Facebook
  Open Graph metadata) which is an improvement over using things like the \texttt{<title>} tag. The
  display of results from these two areas should improve slightly and there may be other sites
  that can receive these improvements as well.

\item \textbf{The search results page should be fully responsive.} The current search results page
  is implemented separately for desktop and mobile. A fully-responsive page would modernise
  the front end, provide opportunities to start incorporating further features around rich snippets
  and give an aesthetic veneer to the more data-driven improvements that are to come.

\end{itemize}

It should be noted that these are \emph{proposed} features. It is fully expected that
most will require specific analysis, prototyping or user validation. The presence of a given
feature on the road map indicates that it will be proven quickly (and fail quickly if it is going to fail)
as early on in its implementation as possible. The understanding is we are willing
to throw away ideas that do not ultimately work.

### 2014-05-15 chapter5.2.tex
Big push into chapter 5. The road map is outline and just needs filled in really. Then summary and review.

\section{Strategy and Technology}

As depicted in figure~\ref{led-indexing-chain}, the architectural
approach is based around discrete, decoupled, RESTful services
forming a conceptual pipeline that takes notification of content
through a process of augmentation, validation and indexing. Recognising
and exploting Conway's Law\cite{conway1968committees}, a good strategy
would be to focus subteams on each major area of the application
(so that the team organisation fits the architecture rather than the
architecture emerging from the team structure).

Features will cut vertically down the entire technology stack, but
the individual engineering tasks to implement them can be split
across subteams focused on each of:

\begin{itemize}
  \item \textbf{Discovery.} This subteam will focus on the URLNotification
    and URLFetch services as well as any integration work upstream to
    generate notifications where such mechanisms do not already exist for certain
    types of content. Typical considerions will be around RSS/Atom feeds that
    might notify of new content, message-based notifications from other
    systems and maintaining a crawler that finds the rest.
  \item \textbf{Enrichment and Inference.} Here the development team will focus
    on integration with BBC or external data sources to enrich information
    coming from the discovery stages. The developers will also need
    to gain sufficient domain knowledge of each content area to make sound
    inferences from the enriched metadata that then generate sensible
    values for fields required by the search indexes.
  \item \textbf{Ingest.} The Ingest API and the search indexes themselves
    will be maintained by a subteam responsible for accepting, validating,
    archiving, indexing and reindexing content. The Ingest API will have
    not just the enrichment stages as a client, but also any BBC team that
    wishes to push its data directly to the search system already transformed.
    Received content will need to be archived in a ``raw'' form so that
    indexes can be reorganised and rebuilt if their structure need to change. It
    is also possible that the archived content might be repushed via the
    enrichment stages to take advantage of new business rules added therein by
    the previous subteam. There is also much work just around designing the
    structure of indexes, configuring linguistic matching and otherwise
    optmising retrieval that it might prove necessary to split out a subteam
    dedicated to those tasks.
  \item \textbf{Results Pages.} This is the subteam dedicated to the front
    end web pages. This is where user experience, design and other front
    end concerns are a primary focus. It is expected that this subteam
    will make requirements for the ingest subteam.
\end{itemize}

The boundaries between subteams do not need to be strict and the team
itself can still behave as a single team sharing ideas, development practices
and tooling. The intention here is to have one or two developers that naturally
gravitate to being responsible for their nominated area so as to encourage
each area to behave in a decoupled way that is built to tolerate failure of
other parts of the system.

The loose coupling afforded by linked data and REST should allow these areas
to evolve independently without changes causes breakages. For example, the
discovery component should be able to generate more linked data through finding
new ways of extracting metadata from content without the enrichment stage
suffering. This in contrast to more brittle RPC-over-HTTP architectures where
an upstream client sending a new XML or JSON format would cause a service to
start rejecting the requests unless the service was updated at the same time.

Introducing some devops responsibilities to the individual subteams and
making use of cloud technology could even permit each subteam to
develop their respective component(s) in different programming languages or
with different frameworks since the components only share information
via HTTP. These are decisions to be made by the developers as they come
to evaluate the best tools for their respective tasks.

### 2014-05-15 chapter5.3.tex
Big push into chapter 5. The road map is outline and just needs filled in really. Then summary and review.

\section{Road Map}

The BBC Search application differs somewhat from many other sites in that
the vast majority of the effort, complexity and codebase lives well
below the HTML/CSS/Javascript surface. The web application side follows
a typical stack comprising Javascript/CSS interface, server-side code/templates
to render the pages and a data layer (the search indexes). However, it has been
shown so far that there are orders of magnitude more complexity upstream
of this data layer, but I hope I have shown that linked data technologies
will reduce some of the unnecessary complexity at least.

This has implicates for planning features, stories, tasks, etc. within
an Agile methodology as the first story to display the most basically
functionality on a web page can easily lead to a wealth of engineering
behind the scenes. In this case, there are a lot of systems already in
place, so this road map will attempt to keep features as iterative as possible.

\subsection{Fully-Response Search Results Page}

% Information Architecture
% Link to D. Marland's article

\subsection{Indexing Programmes Microsites}

% PICR

\subsection{Linking to iPlayer}

% Expiry of content - recrawl/refetch

\subsection{Automatic Curation of Programmes Microsites}

% Editor's Choice - Triplestore
% Can start to curate other things ahead of time
% Publishing tool?

\subsection{Improve Results for Crawled Sites}

% CBBC, K&L

\subsection{Showing Next Broadcast for a Programme}

% More rich snippets

### 2014-05-15 chapter5.3.tex
Starting to working through the plan

@@
 
-% Information Architecture
-% Link to D. Marland's article
+Whilst there are several improvements for end users due to better
+curation of suggested links and rich snippets, minor improvements
+might best be accompanied with more aesthetic changes to increase
+their impact. Also, it is good practice in \emph{Behaviour Driven Development}
+(BDD) to frame changes in terms of desired behavioural changes from
+the perspective of users of the system. To achieve this, the first
+feature to be addressed will be rebuilding a responsive results
+page in parallel to the existing one.
+
+When the new, responsive page is viable for public use, a switchover
+can happen to move people away from the old page. However, this
+switchover does not need to happen until some of the later features
+have been developed. Whether the new, responsive page is in
+use or not, all features will be defined around improvements to
+it.
+
+David Marland stated that the ``core principle in creating a potentially
+enormous website that will last forever is to get the information
+architecture right in the first place'' in discussion around
+building the responsive programmes microsites.\cite{marland2014responsive}
+Given that
+search is also a potentially enormous website driven by of the
+order of millions of data items, it is fitting to map out the
+information architecture in this first feature and use that to
+drive any domain modelling and vocabularies the search application
+needs to use.
+
+Thus this first feature should include some principles of
+\emph{Domain-driven Design}\cite{evans2004domain}
+in that the search team should identify
+a domain model of the search page, the results that appear therein
+and a common vocabulary that can describe those items even if
+they originated in different systems with differing vocabularies.
+
+A common model across differing BBC content items has been
+attempted\cite{fenning2014applicability} at a high level, but
+for first iterations of this feature, a simplistic model
+such as that shown in figure~\ref{fig:initial-onotology}
+would suffice.
 

### 2014-05-16 chapter3.1.tex
Almost finished chapter 4.
More headway with Chapter 5, improved how word counts are done and change RDF graph diagrams to render the DOT via dot2text to make scaling nicer rather than going via PNG.

@@
 \subsection{Current Implementation}
+\label{sec:current-impl}
 
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{question-time.png}
+    \begin{dot2tex}[dot,pgf,scale=0.25]
+      \input{question-time.dot}
+    \end{dot2tex}
   \end{center}
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{politics.png}
+    \begin{dot2tex}[dot,pgf,scale=0.41]
+      \input{politics.dot}
+    \end{dot2tex}
   \end{center}
@@
 Returning to the semantic view of Question Time in figure~\ref{question-time},
-we can see that the page also describes further entities representing
-a \emph{episodes} with identifiers \texttt{bbcprog:b006t1q9\#programme}
-and \texttt{bbcprog:b04446v3\#programmes}. There are a far greater
+we can see that the page also describes another entity representing
+an episode \emph{episodes} with identifier \texttt{bbcprog:b006t1q9\#programme}.
+There are a far greater
 number of episodes linked, but the illustration here is reduced to
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{keepod.png}
+    \begin{dot2tex}[dot,pgf,scale=0.41]
+      \input{keepod.dot}
+    \end{dot2tex}
   \end{center}
@@
   \begin{center}
-    \includegraphics[width=\linewidth]{keepod-tagged.png}
+    \begin{dot2tex}[dot,pgf,scale=0.41]
+      \input{keepod-tagged.dot}
+    \end{dot2tex}
   \end{center}

### 2014-05-16 chapter5.3.tex
More headway with Chapter 5, improved how word counts are done and change RDF graph diagrams to render the DOT via dot2text to make scaling nicer rather than going via PNG.

@@
 
+\begin{figure}
+  \begin{center}
+    \begin{dot2tex}[dot,pgf,scale=0.41]
+      \input{basic-ontology.dot}
+    \end{dot2tex}
+  \end{center}
+  \caption{Basic ontology modelling the traditional ``title, link, description'' search result}
+  \label{fig:initial-ontology}
+\end{figure}
+
 A common model across differing BBC content items has been
@@
 
+The ``Results Page'' subteam can thus focus on initiating
+several iterations of user experience design, user testing
+and development of the results page and it is expected this
+feature will continue to develop in the background as
+other features are worked on by other subteams. It is likely
+individual stories might add to the domain model even
+to make this simple, responsive rebuild of the results page.
+
+The front end application can continue to search the
+existing search indexes independant of any work being done
+to improve the ingest chain. The importance of developing
+this feature first is to ensure the information architecture
+and domain models are defined up front. After this point,
+the other subteams can proceed with the features below
+while the results page developers keep iterating on
+a user interaction that evolves through user testing and
+feedback.
+
 \subsection{Indexing Programmes Microsites}
+
+The ``Ingest'' subteam needs to ensure the Ingest API can
+accept content meeting the basic vocabulary outline in
+figure~\ref{fig:initial-onotologu}, validating ones
+that do not contain the basic fields and evolve the API. If
+the results page developers choose to alter the domain
+model based on design iterations and user feedback, then
+these changes can propogate back as requirements for the
+content ingest.
+
+The team should also evaluate any relevant technologies for the
+search indexes and ensure they are searchable by the
+developers working on the results page.
+
+Elasticsearch is a standalone search server based on Apache Lucene
+that can store, index and retrieve schemaless JSON structures.
+The indexing chain is to deal with RDF graphs, for which JSON-LD
+is a powerful JSON serialisation that can be sent to Elasticsearch
+without any transformation.
+A simple prototype of an ingest function written in Python
+that receives JSON-LD is shown in listing~\ref{lst:ingest}.
+
+\begin{lstlisting}[language=Python]
+from elasticsearch import Elasticsearch
+import json
+
+def ingest_jsonld(jsonld_string):
+  body = {'jsonld': json.loads(jsonld_string)}
+  ElasticSearch().index(index='search', body=body, doc_type='item')
+\label{lst:ingest}
+\end{lstlisting}
+
+The focus for the ingest work should then be around setting
+up mappings in Elasticsearch (if the prototype proves promising)
+to arrange indexes to enable sensible retrieval behaviour.
 

### 2014-05-17 chapter5.3.tex
Sort of finished chapter 5!

@@
 
-The ``Results Page'' subteam can thus focus on initiating
+There are modelling decisions still to be
+made around whether to use this new vocabulary exclusively
+or attempt to follow an existing one such as Schema.org. The
+World Wide Web Consortium (W3C) usually recommends the practice
+of \emph{extending} existing vocabularies over coining new
+ones, but the linked data model always allows us to publish
+mappings to existing vocabularies. However, small, bespoke
+ontologies are arguably easier to define, control and iterate
+in an agile manner and mappings to existing vocabularies
+can be published later.
+
+For the rest of this implementation plan, it is assumed
+the custom ontology described will be used as replacing it
+with equivalent properties from an existing ontology
+is not a difficult task at the point of implementation.
+
+Once the model is decided,
+the ``Results Page'' subteam can thus focus on initiating
 several iterations of user experience design, user testing
@@
 \subsection{Indexing Programmes Microsites}
+
+This feature involves replacing all programmes entries in
+the search indexes with linked data sent through the proposed
+indexing chain. The effect for the front end application
+will be to unify the three separate categories for
+programmes content mentioned in section~\ref{sec:search-results-page}.
+
+In the initial iteration, this will take the form of a single
+``Programmes'' category that simply links to microsites
+for different programme entities. Direct linking to iPlayer
+will be lost temporarily, but restored in the next
+feature. Note that users will always be able to reach
+iPlayer via programmes microsites.
 
@@
   body = {'jsonld': json.loads(jsonld_string)}
-  ElasticSearch().index(index='search', body=body, doc_type='item')
+  ElasticSearch().index(
+    index='search', body=body, doc_type='item')
 \label{lst:ingest}
@@
 
-% PICR
+The \emph{Discovery} subteam will need to investigate
+suitable mechanisms for notifying when certain programmes
+objects have changed. There are asynchronous, message-based
+systems in place witin the BBC specifically around
+programmes change notifications and the engineered solution
+is likely to make use of that.
+
+Alongside this work, those responsible for enrichment and
+inference will need to define (and apply) the rules for
+mapping the vocabularies used by programmes microsites
+to the ontology and vocabulary used in the search application.
+Such rules will extend the form introduced in
+section~\ref{sec:ld-indexing}.
 
@@
 
-% Expiry of content - recrawl/refetch
+In this feature, direct links to iPlayer are added back into
+search results for programmes.
+
+One difficulty is around
+the temporal nature of programmes information. The graph
+shown back in figure~\ref{question-time} shows
+the time of the next broadcast, but that information will
+soon expire and the search system might be interested in
+reindexing that programme when the nature of its availability
+on BBC iPlayer changes.
+
+It is thus likely that the Discovery subteam working on the
+URLNotification component will need to develop components
+that query an archive of the linked data ingested to look
+for items that may need reingested. They may need to
+place requirements on the Ingest team to store an archive
+of the linked data within a \emph{triple store} or other
+data store (note that Elasticsearch has been known to be
+suitable to act as both a search service and a NoSQL-style
+document store in one). It is then a decision for teh
+engineers as to whether complex SPARQL queries can mine
+for programmes (or indeed any) content that has passed
+a significant point of time at which the information becomes
+out of date or whether to augment the simple ontology
+in figure~\ref{fig:basic-ontology} with the concept of
+a search result's information \emph{expiring} as shown in
+figure~\ref{fig:expiring-ontology}.
+
+\begin{figure}
+  \begin{center}
+    \begin{dot2tex}[dot,pgf,scale=0.41]
+      \input{expiring-ontology.dot}
+    \end{dot2tex}
+  \end{center}
+  \caption{Concept of a potential search result's information expiring has been added}
+  \label{fig:expiring-ontology}
+\end{figure}
+
+This expiry concept is not necessarily that the content item
+should no longer appear in the search indexes, but that the
+information should be considered stale and refetching the data
+is recommended. This is not too far removed from Google
+recrawling pages based on some assessment of how often the page
+should be checked, but here we can use the semantic metadata
+available publicly (and indeed internally) to get a more
+precise idea of a good expiry date.
+
+At this stage, it could
+be proposed to send a notification to the URLNotification
+component a short time after the date and time within the
+value of \emph{any}
+\texttt{http://schema.org/endDate} property has passed. A more
+suitable strategy might emerge as the individual user stories
+within this feature are planned out by the development team.
 
@@
 
-% Editor's Choice - Triplestore
-% Can start to curate other things ahead of time
-% Publishing tool?
+The current Editor's Choice feature links to the top-level
+brand microsite (e.g. the home page for \emph{Question Time})
+for any programme, but generally does not link to the pages
+for specific series/seasons nor individual episodes. This gives
+rise to that idea that something modelled as a potential
+search result in our domain model \emph{may} be a recommended
+result, but not all results have this property. This can
+lead to the next iteration of the domain model/ontology in
+figure~\ref{fig:recommended-ontology}, which introduces a
+property that indicates when a \texttt{:SearchResult}
+can be said to represent a recommended page for any concept.
+For instance, the URI for Question Time as a concept
+will have the recommended page of the microsite about that
+programme.
+
+\begin{figure}
+  \begin{center}
+    \begin{dot2tex}[dot,pgf,scale=0.41]
+      \input{recommended-ontology.dot}
+    \end{dot2tex}
+  \end{center}
+  \caption{Ontology augmented with the concept of a recommended link for an entity}
+  \label{fig:recommended-ontology}
+\end{figure}
+
+The Ingest subteam should then look at maintaining a second
+index of just the names/titles of potential search results
+that are marked as ones that might be recommended. The
+results page front end subteam can then focus on being
+able to query both this new index and the index of documents
+so as to render Editor's Choice and organic search results
+links respectively on a single page.
+
+The API through which the front end web application queries for
+these recommended links can not only expose these recommendations
+as linked data, but also allow an administrative application
+to create, maintain and remove recommendations should there
+be requirements from editorial staff to be able to do so. In this
+case, we should revisit the domain model (i.e. iterate it further)
+to distinguish between, say, \texttt{:automaticRecommendedLink}
+which prompts editorial staff to create a corresponding
+\texttt{:approvedRecommendedLink}. This reflects the typical
+workflows in editorial web tools that traditionally store unmoderated,
+approved, etc. links, but instead encourages through the use of RDF
+to publish this as linked data by default. This again follows the
+principles of linked enterprise data laid out in chapter~\ref{stateoftheart}.
+
+The developers working on inference should gather requirements
+for inferring recommendations from the upstream RDF graphs,
+which in the case of programmes apparently follows from simply
+creating a recommendation for any programme brand to its
+respective ``home page'' or microsite.
 
@@
 
-% CBBC, K&L
+The next feature should address removing configuration for
+some actively-maintained BBC sites -- such as CBBC and
+Knowledge and Learning -- from the existing web crawler
+application and instead push discovered URLs through the new
+RDF-based indexing chain. The developers working on discovery
+should look to push notifications of new, changed and removed
+pages to the URLNotification service, even if they originate
+from a web crawler.
+
+The enrichment components could be extended to fetch additional
+metadata by integrating against backend services that drive
+these sites. Investigations will need to be made around this,
+but any new information that can be added will be an improvement
+over the current way the sites are simply web crawled and scraped.
+
+It is not expected that the domain model should need to change
+significantly, so the ingest and results page applications may not
+need specific changes, but it is expected that the presentation
+of, e.g. the titles, in the search results for these sites will look
+cleaner by properly ascertaining the metadata as opposed to relying
+on web scraping to takes things out of HTML tags (e.g. the \texttt{<title>}
+tag.
+
+This feature is intentionally not specified with as much detail
+as the previous features as agile methodologies usually encourage
+making most decisions when closer to implementation of the feature, at
+which point there may be a lot more information available.
 
@@
 
-% More rich snippets
+This is another feature that is not over-specified, but it does
+clearly follow from the ability to add BBC iPlayer links to
+programmes search results that it should be possible to decorate
+those results further with a quick indication of when that
+programme is next broadcast on a TV or radio service.
+
+The information should already be present in the RDF graphs being indexed,
+so this work is theoretically just focused around those developers
+working on the search results web application to generate such
+decoration in the presentation layers based on information that is
+already present in the search indexes.

### 2014-05-17 chapter5.4.tex
Added a wrap-up to chapter 5.

\section{Future Iterations}

The continuing strategy is to move all existing indexing systems into
this RDF-based indexing chain, but also to drive the changes with
tangible improvements visible to users on the results page itself.

In following agile principles, it is remaining out of scope for this
proposal to suggest features beyond those already presented. At a time
where most of these features are implemented, the problem space and
landscape may have changed enough that the road map presented would
have to react to these changes. It is possible that this reaction to
change may have to occur before the described features are fully implemented.

### 2014-05-18 chapter6.tex
Finished summary. Time to review.

\chapter{Summary}

The shift from enterprise integration to linked enterprise data
seems particulary suitable for the BBC given the legacy of
distinct data sources that has built up over time. It is hoped that
the search application can act as a strong example of the advatanges
of publishing enterprise data as linked data and that integration
costs can significantly reduce as a result.

It was noted in section~\ref{sec:current-impl} that global search
engines such as Google create a pressure on websites to structure
their pages in certain ways and even to include semantic metadata. A
search application that makes this metadata the foundation of its
discovery and indexing processes (even if mixed with some direct integration
for data enrichment) might create additional pressures on BBC websites
to not only include more of their business data in public pages, but
also to link that data to related content in other sites.x

A search application that bases its indexing in linked data and
web standards should be more agile and this will open up opportunities
to innovate on features visible to the users more rapidly.

Future analysis is recommended to address auxillary features such as
the autocomplete\cite{morville2010search} feature that appears when a user
is typing in
the search box. Much of this data is manually-maintained as is the case
with Editor's Choice. Future work should be able to look into a suitable
combination of automatic inference and manual curation to collate
possible autocomplete or autosuggest searches and links with the need to
maintain the whole list of potential completions by hand. This should follow
naturally from the work on Editor's Choice, but the autocomplete
improvements should
be designed after any lessons are learnt from the Editor's Choice development.

The search application should endeavour to publish its own information
as linked data as well, where data are created. Examples include publishing
curation of recommended links or perhaps the application could create
pages that link and aggregate content around a topic or concept. Such an
approach could have powerful implications for the search application being
at the centre of breaking down silos across the BBC and being a central
place for users to make horizontal journeys between related content.

Further studies, analsys and proposals after implementations of this proposal
are recommended to investigate the benefits of linking more data
between the content on different BBC sites.

### 2014-05-19 chapter1.tex
Did some reviewing and trrying to fit diagrams in.

@@
   \item Further decoupling of BBC applications, which aids scalability,
-    maintainability and resilience in many software architectures.\cite{}
+    maintainability and resilience in many software architectures.
   \item Improvements to the search results page that help users determine
-    if the results given are relevant via so-called
+    if the results given are relevant. The example of this is by using
     \emph{Rich Snippets}\cite{goel2009introducing}
@@
     where semantic properties about the results can drive visual decoration
-    and calls to action, which can allow for a more flexible and
-    adaptable design without the need to enumerate all ``kinds'' with
-    different templates.
-  \item Removal of the manual curation of the ``Editor's Choice'' results
+    and calls to action.
+  \item Removal of the exclusively manual curation of the ``Editor's Choice'' results
     against a given query and replacing it with curated linked data that
@@
 In the rest of this chapter, I will give an overview of what role BBC
-Search plays and how we can usefully view the system as four
-distinct subsystems. In later chapters we can then look to improve these
-four separate systems one at a time and then evaluate how these improvements
-might complement each other.
+Search plays and the distinct subsystems that it comprises.
+In later chapters we can then look to improve these systems
+how these improvements might complement each other.
 
@@
 
+\section{Indexing Content}
+
 It is well established that a classical information retrieval system
@@
 users submitting queries in a single second.
-
-In the remaining sections of this chapter, I outline the considerations
-around these two sides of the search application in addition to the
-two complementary systems known as \emph{Editor's Choice} and
-\emph{Search Suggest}.
-
-\section{Indexing Content}
-
-% TODO
 
@@
 Note that a system could trivially maximise recall by always returning all
-results, but such a system would perform poorly in terms of precision. A
-measure known as \emph{F-measure} was derived by van Rijsbergen
-\cite{rijsbergen1979information} which
-balances precision recall based on preferring recall over precision $\beta$
-times:
+results, but such a system would perform poorly in terms of precision.
+This makes a search application a delicate balance of trying to show
+users as much of what they want as possible without cluttering the results
+with irrelevant items.
 
-\begin{displaymath}
-  F_\beta = (1 + \beta^2) \cdot \frac{\mathrm{precision} \cdot \mathrm{recall} }{ \beta^2 \cdot \mathrm{precision} + \mathrm{recall}}
-\end{displaymath}
-
-There are other measures such as average precision and average mean precision
-that take into account ordering of results and the average over multiple
-queries respectively. A successful algorithm or third party search engine
-application can be evaluated quantitatively by these measures and more. A more
-qualitative summary from the perspective of the end users could be:
-
-\begin{quote}
-  A successful search application will return only the content the user wants
-  (precision) --
-  as high up the results list as possible -- and as much of desired content
-  as possible (recall).
-\end{quote}
+The task is complicated somewhat further from a user experience perspective
+if an application wishes to attempt to create \emph{serendipity}. The
+concept of serendipity -- showing the user something they were not looking
+for, but turns into a positive onward journey -- is recognised
+as part of the search user experience and is something human-computer
+interaction designers try to aspire to create.\cite{russell2012designing}
 
@@
 the BBC Weather page for Coventry.
-
-\section{Summary}
-
-In chapter~\ref{stateoftheart} I will briefly outline some of the state of the
-art in the Linked Data domain and start to highlight areas that show
-the most promise for improving the four areas of the search application
-described in this chapter.

### 2014-05-19 chapter2.tex
Did some reviewing and trrying to fit diagrams in.

@@
 \begin{enumerate}
-  \item Use URIs to denote things.
-  \item Prefer HTTP URIs (i.e. URLs) so that these things can be looked
-    up (i.e. \emph{dereferenced}.
+\item Use URIs to denote things, whether pages/documents on the web
+  or real physical and conceptual things in the world.
+\item Prefer HTTP URIs (i.e. URLs) so that they can be looked
+  up (i.e. \emph{dereferenced} to get more information about the thing denoted.
 \item When these URIs are dereferenced, provide useful information about
-    those things using standards.
+  those things using web standards, e.g. RDF, HTML, XML, Turtle.
 \item Include links to other things (using their URIs) when such
@@
 
-It can be seen as a subset of Semantic Web techniques and it builds upon
+This overlaps somewhat Semantic Web techniques and it builds upon
 the \emph{Resource Description Framework} (RDF)\cite{lassila1999resource},
@@
 data may be used within an enterprise setting to reduce traditional
-integration efforts and then touch on some other aspects of the linked
+integration efforts Finally, I will then touch on some other aspects of the linked
 data domain that could be of interest to the search application.
@@
   \item DC-HTML defines how to embed the Dublin Core vocabulary within HTML
-    meta tags.
-  \item Microdata is an HTML standard that allows annotating existing markup
+    meta tags.\cite{johnston2008expressing}
+  \item Microdata\cite{htmlstandard} is an HTML standard that allows
+    annotating existing markup
     via additional attributes so that it serves as metadata in addition to
@@
 \emph{JSON-LD} format within HTML \texttt{<script>} tags to add semantic
-information alongside textual data, but without annotating this metadata
+information alongside textual data, but without needing to annotate this metadata
 around the textual content itself as we would with RDFa, for example.
@@
 All of the above approaches can be found ``in the wild'' in pages across
-the Web with differing rates of adoption. General-purpose web search
+the Web with differing rates of adoption.\cite{haas2011enhanced}
+General-purpose web search
 engines can make use of this additional metadata to improve the quality
@@
 then our search application can match on this auxiliary information.
+
+This is out of scope for this paper, but
+is recommended as a further study after this proposal has been implemented.
 
@@
 and incentive on web publishers to include semantic metadata in their web
-content if they aspire to attacting visitors via global search engines such
+content if they aspire to attracting visitors via global search engines such
 as Google, Bing and Yahoo!.
@@
 a major motivation of Linked Data being that it aids in breaking
-down information silos.\cite{bizer2009linked} In the
-\emph{Linked Enterprise Data} approach, all information
-production remains \emph{distributed} but is
+down information silos.\cite{bizer2009linked} The key theme
+in the \emph{Linked Enterprise Data} approach is that all information
+production remains \emph{distributed} but becomes
 \emph{connectable}.\cite{allemang2010semantic}
 
-An organisation that seeks to ensure that all information is
-published as Linked Data can learn from examples such as Wikipedia
--- or indeed the web in general -- where individual experts are
-encouraged to share knowledge rather than keep it in silos. This
-distributed approach recognises that diversity and flux are the
-steady state of an agile enterprise. Two sources that happen
-to use the same vocabulary are instantly interoperable. Two
-sources that use a different vocabulary could well be integrated
-simply by creating appropriate mappings between the vocabularies.
-It should not be necessary to re-engineer a whole dataset nor
-create entirely new systems just for integration.
+A distributed
+approach to such publishing across an enterprise keeps data sources
+interoperable, but allows them to develop and grow independantly. This
+recognises that such flux and diversity is the steady state of
+an agile enterprise and shows that attempts to impose a controlled
+data store and vocabulary across the enterprise are doomed to fail.
+Integration of two previously-disconnected data sources is simply
+a matter of creating appropriate vocabulary mappings. It is no
+longer necessarily to build bespoke middleware or rebuild one or
+both data stores.
 
@@
 
-\begin{comment}
+\section{Linked Data and Search}
+
 If we view the indexing processes
@@
 integration.
-\end{comment}

### 2014-05-19 chapter4.1.tex
Almost finished chapter 4.
Did some reviewing and trrying to fit diagrams in.

@@
 \section{Linked Data Indexing}
+\label{sec:ld-indexing}
 
@@
 
+Whilst the enrichment stage means we have not fully eliminated the
+need for bespoke integration work, the important factor to consider is that
+such integration is no longer \emph{required}. If basic properties
+are sourced upstream from the public web page, then the lack
+of ability to integration -- or if that integration breaks, as brittle,
+coupled integration applications are prone to do -- then the information
+can still be passed through to retain a \emph{degraded} search
+experience. This is preferable to the complete loss of an upstream feed
+due to incompatible changes being made unannounced.
+
 The next stage is to run the RDF graph through an \emph{Inference} process.

### 2014-05-19 chapter5.3.tex
Did some reviewing and trrying to fit diagrams in.

@@
   \begin{center}
-    \begin{dot2tex}[dot,pgf,scale=0.41]
+    \begin{dot2tex}[dot,pgf,scale=0.42,options=-traw]
       \input{basic-ontology.dot}
@@
   \end{center}
-  \caption{Basic ontology modelling the traditional ``title, link, description'' search result}
-  \label{fig:initial-ontology}
+  \caption{Basic ontology modelling the traditional ``title, link, description'' search result\label{fig:initial-ontology}}
 \end{figure}
@@
 for first iterations of this feature, a simplistic model
-such as that shown in figure~\ref{fig:initial-onotology}
+such as that shown in figure~\ref{fig:initial-ontology}
 would suffice.
@@
 accept content meeting the basic vocabulary outline in
-figure~\ref{fig:initial-onotologu}, validating ones
+figure~\ref{fig:initial-ontology}, validating ones
 that do not contain the basic fields and evolve the API. If
@@
 
-\begin{lstlisting}[language=Python]
+\begin{lstlisting}[language=Python,label=lst:ingest]
 from elasticsearch import Elasticsearch
@@
     index='search', body=body, doc_type='item')
-\label{lst:ingest}
 \end{lstlisting}

### 2014-05-20 chapter1.tex
Done! Reviewed and ready to submit.

@@
     and calls to action.
-  \item Removal of the exclusively manual curation of the ``Editor's Choice'' results
+  \item More automation of the curation of the ``Editor's Choice'' results
     against a given query and replacing it with curated linked data that
@@
 
-In the rest of this chapter, I will give an overview of what role BBC
+In the rest of this chapter, I will give an overview of what r\^ole BBC
 Search plays and the distinct subsystems that it comprises.
@@
   \textbf{recall} = \frac{
-    |{relevant documents} \cap \text{retrieved documents}|
+    |\text{relevant documents} \cap \text{retrieved documents}|
   }{

### 2014-05-20 chapter2.tex
Done! Reviewed and ready to submit.

@@
 \item Use URIs to denote things, whether pages/documents on the web
-  or real physical and conceptual things in the world.
+  or real, physical and conceptual things in the world.
 \item Prefer HTTP URIs (i.e. URLs) so that they can be looked
-  up (i.e. \emph{dereferenced} to get more information about the thing denoted.
+  up (i.e. \emph{dereferenced}) to get more information about the thing denoted.
 \item When these URIs are dereferenced, provide useful information about
@@
 
-This overlaps somewhat Semantic Web techniques and it builds upon
+This overlaps somewhat with Semantic Web techniques and it builds upon
 the \emph{Resource Description Framework} (RDF)\cite{lassila1999resource},
@@
 a comprehensive ``Web of Data'' to rival the rich, so-called
-``Web of Documents'' that is the World Wide Web as we know it as a collection
+``Web of Documents'' that is the World Wide Web as we know it -- a collection
 of human-readable pages.
@@
 of the search results in a number of ways. In section~\ref{enhancing-results},
-I discuss some of these potential improvements.
+some of these potential improvements are discussed.
 
@@
 snippet may sometimes present incorrect information (e.g. showing the wrong
-price for a product is less preferable than simply not attempting to present
+price for a product is less preferable to simply not attempting to present
 the price at all). Implicit feedback via click-through rates (CTR) --
@@
 
-\emph{Enterprise integration} is an important technical field within the
-discipline of Enterprise Architecture that focuses on interconnecting
+\emph{Enterprise Integration} is an important technical field within the
+discipline of \emph{Enterprise Architecture} that focuses on interconnecting
 systems and allowing data to flow between them. This can be seen as
@@
 
-There are difficulties with some of these approaches noted by
+However, There are difficulties with some of these approaches -- as noted by
 Allemang\cite{allemang2010semantic}. Data warehousing,
@@
 linked data as a more cost effective means of building search
+indexes that bring together all published content.
 

### 2014-05-20 chapter3.1.tex
Did some reviewing and trrying to fit diagrams in.
Done! Reviewed and ready to submit.

@@
 
-We can achieve some uniformity of the data by building a single, common
+Some uniformity of the data is achieved by a single, common
 API through which all content is fed into the Search application. However,
@@
   \begin{center}
-\begin{dot2tex}[dot,scale=0.6]
+\begin{dot2tex}[dot,scale=0.7]
 digraph ingest {
@@
 
+  subgraph cluster_0 {
+    label = "BBC Websites";
     Programmes [shape=rect]
@@
     Sport [shape=rect]
-  MarketData [shape=rect]
-  WorldService [shape=rect]
-  BBCFood [shape=rect]
-  ProgrammesWebsites [shape=rect]
-  LegacyWebsites [shape=rect]
+    MarketData [shape=rect,label="Market Data"]
+    WorldService [shape=rect,label="World Service"]
+    BBCFood [shape=rect,label="BBC Food"]
+    ProgrammesWebsites [shape=rect,label="Programmes Microsites"]
+    LegacyWebsites [shape=rect,label="Legacy Websites"]
+  }
 
+  subgraph cluster_1 {
+    label = "Search Application";
+    FileBasedQueues [label="Message Queues"]
+    IngestAPI [label="Ingest API"]
     SearchIndexes [shape=circle]
+    Crawler
+    trans2 [label="Transformation"]
+    Transformation
+  }
+
+  subgraph cluster_2 {
+    Dynamite
+    CPS
+    label = "Back-end Services";
+  }
 
@@
   LegacyWebsites -> Crawler
-  trans2 [label="Transformation"]
   Crawler -> trans2
@@
 key system whose primary r\^ole is to break down all the content silos in the
-BBC, which was noted as a motivation for Linked Data in chapter 2.
+BBC. This aligns with the one of the major motivations of linked data, which
+is to break down content silos within organisations or indeed globally.
 
-There is also an apparent requirement that we are cautious of delegating
-too much integration work to other teams. From the perspective of teams
+It seems there needs to be consideration around balancing the amount of
+integration work delegated to other teams. From the perspective of teams
 whose products produce content, the ideal search system would be
@@
 
-\subsection{The Content}
+\section{The Content}
 \label{content}
@@
 The front end search application currently divides all the searchable
-content into so-called ``zones''. Table~\ref{zones-table}
+content into so-called ``zones''. Table~\ref{zones-table} explains
+each of these categories.
 
-%TODO - is this all of them?
-\begin{sidewaysfigure}
+\begin{sidewaystable}
   \centering
@@
   \hline
-  CBBC                   &  Pages, games, programmes information for Children. Some semantic markup exists for Facebook's Open Graph. \\
+  CBBC                   &  Pages, games, programmes information for Children. Has semantic markup for Facebook's Open Graph. \\
   \hline
@@
   \hline
-  Health \& Parenting    &  \\
+  Health \& Parenting    &  Websites about health, pregnancy, relationships, etc.
+Most have been left unchanged for several years and some have in fact been taken down, but entries still exist for the removed pages in the search indexes.
+\\
   \hline
-  History                &  \\
+  History                &  A mixture of legacy sites relating to history and a revamped History home page until the banner of the new ``Knowledge and Learning'' collection of sites. \\
   \hline
-  iPlayer                &  \\
+  iPlayer                &  On-demand catch-up service for TV and Radio programmes broadcast on the BBC.
+Videos are traditionally only available for 7 days (this will change to 30 days soon) after broadcast.
+\\
   \hline
-  Learning               &  \\
+  Learning               &  A vast collection of websites with learning materials for children and adults alike.
+The content varies from very old pages to maintained ones revamped under the ``Knowledge and Learning'' brand.\\
   \hline
-  Local (archive)        &  \\
+  Local (archive)        &  Legacy pages aimed at different local areas of the UK.
+Newer content is generally under the remit of BBC News, which has sections for different UK regions and local news therein.
+\\
   \hline
-  Music                  &  \\
+  Music                  &  Sites about music artists, reviews of albums, BBC orchestras, etc.
+The artist pages are driven by semantic metadata (e.g.
+Musicbrainz, DBPedia), but only markup for Facebook's Open Graph occurs in the pages.\\
   \hline
-  News                   &  \\
+  News                   &  News articles published over several years. The quality of the pages and the markup varies with the age of the content, but newer articles contain some semantic markup. \\
   \hline
-  Ouch!                  &  \\
+  Ouch!                  &  Legacy posts for BBC's blog about disability. From April 2013, blogs became part of BBC News, but links to older posts remain in the indexes. \\
   \hline
-  Religion \& Ethics     &  \\
+  Religion \& Ethics     &  Website under the ``Knowledge and Learning'' giving information on religion, culture and traditions. \\
   \hline
-  Science \& Nature      &  \\
+  Science \& Nature      &  Old and new sites including the maintained Nature site, which uses semantic data to generate a lot of the content\cite{raimond2010use}, and the Science site -- another site under the ``Knowledge and Learning'' brand.
+\\
   \hline
-  Sport                  &  \\
+  Sport                  &  Up-to-date articles and information about sport.
+BBC Sport some similarities with BBC News in terms of articles, but also has some more quantitative data such as match results and fixture dates.
+\\
   \hline
-  Teenagers              &  \\
+  Teenagers              &  Legacy ``Switch'' site aimed at teenagers covering music, TV and games. \\
   \hline
-  TV \& Radio Programmes &  \\
+  TV \& Radio Programmes &  Programmes microsites for every programme, individual episodes and additional content such as clips and character information.
+This content is obtained currently by crawling.
+\\
   \hline
-  TV \& Radio Sites      &  \\
+  TV \& Radio Sites      &  Crawled ``home'' pages for BBC TV and Radio services with crawled, legacy pages about BBC programmes before the common platform for programmes microsites was developed.\cite{raimond2010use} \\
   \hline
@@
 \label{zones-table}
-\end{sidewaysfigure}
+\end{sidewaystable}
 
@@
 crawling. Some active sites are syndicated via RSS/Atom, but a subscription-based
-feed does not allow indexing a backfill of content easily.
+feed does not allow indexing a back-fill of content easily.
 
@@
 knowledge and business rules about the BBC's own online content
-is a way a BBC-specific search product can gather information publically-available
+is a way a BBC-specific search product can gather information publicly-available
 as linked data, but in a more considered way and have advantages over
@@
   \begin{center}
-    \begin{dot2tex}[dot,pgf,scale=0.25]
+    \begin{tikzpicture}[scale=0.35,transform shape]
+    \begin{dot2tex}[dot,pgf,codeonly]
       \input{question-time.dot}
     \end{dot2tex}
+    \end{tikzpicture}
   \end{center}
@@
 different lengths, which might form part of a snippet. We are also
-told that the programme falls within \emph{genres} indentified
+told that the programme falls within \emph{genres} identified
 by \texttt{bbcprog:genres/factual/politics\#genre} and
@@
 clear enough to a human reader to represent a \emph{Politics}
-subgenre (underneath a \emph{Factual} genre) and a
+sub-genre (underneath a \emph{Factual} genre) and a
 \emph{News} genre respectively. However, if we wish to make
@@
 
-Following the politics subgenre URL, we can produce the
+Following the politics sub-genre URL, we can produce the
 semantic representation shown in figure~\ref{politics}.
@@
   \begin{center}
-    \begin{dot2tex}[dot,pgf,scale=0.41]
+    \begin{tikzpicture}[scale=0.6,transform shape]
+    \begin{dot2tex}[dot,pgf,codeonly]
       \input{politics.dot}
     \end{dot2tex}
+    \end{tikzpicture}
   \end{center}
@@
 The time and date of the next broadcast of this episode is also shown.
-From the graph depicted, we can see there is a (presumably repeat)
+From the graph depicted, we can see there is a
 broadcast to occur on Sunday, 11 May 2014 on the BBC Parliament
@@
 search results that might well answer some queries directly
-such as ``When it Question Time next on TV?''. This is similar
+such as ``When is Question Time next on TV?''. This is similar
 to functionality offered by Google where currency conversions,
@@
 
-Finally, note there is some metadata about the pages themselves
+Finally, note there are some metadata about the pages themselves
 that are repeated within the Open Graph protocol namespace
@@
 Overall, there are a lot of metadata obtainable about BBC
-programmes via semantic markup available on the public web. There is
+programmes via semantic markup available on the public web.
+However, there is
 still some information that we cannot obtain:
@@
   \item We cannot easily gather a list of all identifiers that might
-    be interesting to the search application. Crawling links is
-    popular with web crawlers, but there is no guarantee of finding
+    be interesting to the search application. Crawling links with
+    web crawlers is one approach, but there is no guarantee of finding
     everything and there are difficulties knowing when to get an
@@
 chose not to respond with the programme at all under the
-impression it is not available to watch, then there is an
-arguably more broken user experience.
+impression it is not available to watch, then there is
+arguably a more broken user experience.
 
@@
 search indexes. Care should be taken around any design element
-or feature that is affected the lack of information. Ideally,
+or feature that is affected by the lack of information. Ideally,
 all behaviour would follow a \emph{progressive enhancement} model
@@
 
-The programmes dataset is normally the most structured and
+The programmes data set is normally the most structured and
 complex to work with, but is one of the leading uses of
 semantic web technologies on the BBC website as a whole. In
-the rest of this sectio, I will briefly touch on any different
-challenges from other datasets.
+the rest of this section, I will briefly touch on any different
+challenges from other data sets.
 
@@
 The semantic metadata that can be found in a BBC News article
-page is notably less complex that a programmes microsite, as
+page is notably less complex than a programmes microsite, as
 can be seen in figure~\ref{keepod}.
@@
   \begin{center}
-    \begin{dot2tex}[dot,pgf,scale=0.41]
+    \begin{tikzpicture}[scale=0.5,transform shape]
+    \begin{dot2tex}[dot,pgf,codeonly]
       \input{keepod.dot}
     \end{dot2tex}
+    \end{tikzpicture}
   \end{center}
@@
 
-As discusseed in section~\ref{programmes}, BBC News also makes
+As discussed in section~\ref{programmes}, BBC News also makes
 use of Facebook's Open Graph metadata and a search application
@@
   \begin{center}
-    \begin{dot2tex}[dot,pgf,scale=0.41]
+    \begin{tikzpicture}[scale=0.41,transform shape]
+    \begin{dot2tex}[dot,pgf,codeonly]
       \input{keepod-tagged.dot}
     \end{dot2tex}
+    \end{tikzpicture}
   \end{center}
@@
 One remaining piece of information that is still lacking is
-what News category in which the article falls. The BBC News
+the News category in which the article falls. The BBC News
 website has business rules around categorising all news
@@
 
-%TODO - Finish this
+The BBC Sport website shares a lot with BBC News in that a large
+amount of the content is article-based. However, the sport domain
+has a lot of structured data beneath the surface: atheletes,
+teams, competitions, disciplines, events, etc.
+
+An ontology was defined to drive some automatically aggregated
+pages during the 2012 Olympics\cite{rayfield2011bbc}, but reading
+semantic data from a typical article yields a picture very similar
+to the News story example in figure~\ref{keepod}.
+
+There is a lot of potential for structured data to create an
+intelligent search experience whereby, for example, searching
+for a football team by name would suggest links to the last
+match results, dates of when they are next playing or even
+summarise the current league table for the relevant football
+league. This is something for much later than the proposed
+road map in this paper, but it can be hoped that improvements
+from using linked data in other areas of the BBC can inspire
+some interesting collaboration with the BBC Sport teams.
+
+\subsection{Knowledge and Learning}
+
+The ``Knowledge and Learning'' brand is an attempt to create
+a consistent and cohesive picture of what was a discrete
+collection of sites. Topics search as school curricula, revision
+guides, science, religion, food and history have structured
+domain models behind them, but there are limited semantic data
+within the pages themselves. This means the best option for
+the current search application is to run a web crawler across
+these sites, but there are some efforts to create relevant
+ontologies to drive these sites.
+
+One example is the the \emph{Education} website that has
+a distinct page for every school stage, school subject
+and topic within a subject for all the the UK. These pages
+are driven off a domain model and ontology\cite{bbc2013curriculum}
+behind the scenes
+(i.e. it's not present within the HTML pages), but that
+model has been published under a free licence.
+\cite{bbc2014curriculum} This freely-available data set
+effectively acts as site map of the Education website.
+
+\subsection{Legacy Sites}
+
+With websites that are no longer maintained, there is little choice
+but to run web crawlers over these pages. Further complication
+comes from the fact that certain pages may be taken down
+altogether without the search application necessarily being
+notified, so the crawler has to periodically check on
+pages already indexed to confirm they are still there.

### 2014-05-20 chapter3.2.tex
Sort of finished chapter 5!
Done! Reviewed and ready to submit.

@@
 \section{Search Results Page}
+\label{sec:search-results-page}
 
 The majority of the complexity and development arguably lies within
-the indexing processes of the search applicatio, but it is with the
-\emph{actual Search Engine Results Page} (SERP) that the website users interact.
+the indexing processes of the search application, but it is with the actual
+\emph{Search Engine Results Page} (SERP) with which the website users interact.
 
@@
 
-The different categories/zones are shown on the left menu, with the
+In figure~\ref{fig:search-page},
+the different categories/zones are shown on the left menu, with the
 number of results found within each category also shown. The first results
@@
 is a distinct feature to the ``organic'' results that follow below.
-
-The organic results are broken into categories such that this ``All Results''
-page reached after a search acts as a way to skim over each relevant
-category.
 
@@
 
-There is a feature of the current search application where data or metadata
+There is also a feature of the current search application where data or metadata
 are more directly published and that is the ``Editor's Choice'' feature. In

### 2014-05-20 chapter3.3.tex
Done! Reviewed and ready to submit.

@@
 can aid these activities. It is to serve the \emph{Lookup} activity
-that the so-called organic results are header with up to three
+that the so-called organic results are headed with up to three
 ``Editor's Choice'' links that -- based on the query given -- may
@@
 
-Two such distinct modules on the page allow both lookup- and exploration-
+Having both the organic results and the Editor's Choice links
+allow both lookup- and exploration-
 style interactions to occur on the same results page. It could be said
@@
 The Editor's Choice feature assures that common -- or easily recognisable -- queries
-lead to a mix of mechanically-chosen and editorially-curated links,
+lead editorially-curated links in addition to algorithmically-chosen pages,
 with the intention this provides a balance between the large-scale
@@
 
-Howver, each and every link promoted within this feature is hand-chosen by editorial
+However, each and every link promoted within this feature is hand-chosen by editorial
 staff and much manual effort is needed to keep promoting new concepts

### 2014-05-20 chapter4.1.tex
Done! Reviewed and ready to submit.

@@
 
-\begin{figure}
+\begin{figure}[t]
   \begin{center}
@@
 and retains the use case where content producers wish to have full
-control of what metadata is sent to the search indexed -- as long as
+control of what metadata is sent to the search indexes -- as long as
 they are willing to do the integration work.
@@
 information to display search results. It is proposed that these minimal
-graphs will take the form of the following example (in JSON-LD serialisation):
+graphs will take the form of the example (in JSON-LD serialisation)
+shown in listing~\ref{lst:minimal}.
 
 \begin{centering}
-\begin{lstlisting}[language=json]
-[
+\begin{lstlisting}[language=json,label=lst:minimal,caption=Minimal RDF graph in JSON-LD showing only that something exists and a single identifier for it.]
 {
   "@id": "http://www.bbc.co.uk/news/technology-27346567",
-    "http://purl.org/dc/terms/identifier": [
-      {
+  "http://purl.org/dc/terms/identifier": {
     "@value": "http://www.bbc.co.uk/news/technology-27346567"
   }
-    ]
 }
-]
 \end{lstlisting}
@@
 dereferencing is not possible, but the \emph{URLFetch} stage could
-passively send the graph onwards without augmenting to it.
+passively send the graph onward without augmenting to it.
 
@@
 
-The URLFetch service can then send the augmented graph onwards to
+The URLFetch service can then send the augmented graph onward to
 the \emph{Enrichment} service. The purpose of this stage is to apply
@@
 
-In the Enrichment service, we might, for example, contact backend
-service applications for futher data about the content we are trying to ingest.
+In the Enrichment service, we might, for example, contact back-end
+service applications for further data about the content we are trying to ingest.
 This might mean fetching information about a programme from services
@@
 are sourced upstream from the public web page, then the lack
-of ability to integration -- or if that integration breaks, as brittle,
+of ability to integrate -- or if that integration breaks, as brittle,
 coupled integration applications are prone to do -- then the information
@@
 This is where custom rules are invoked to handle the different
-vocabularies that might be in use. For example, the rule shown below
+vocabularies that might be in use. For example, the rule shown in
+listing~\ref{lst:headline-rules}
 (in N3 format) would allow us to infer that we can
@@
 \begin{centering}
-\begin{lstlisting}[language=ttl]
+\begin{lstlisting}[language=ttl,label=lst:headline-rules,caption=Simple inference rules to derive a suitable headline from two different vocabularies.]
 @prefix schema: <http://schema.org/> .
@@
 enterprise integration efforts. In bespoke integration applications, explicit
-transformation would be used to translated  ``news item'' to a
+transformation would be used to translate a ``news item'' to a
 ``search item'' including the rule that explicitly extracted the
@@
 transformation does not need to occur at any syntactic level and we
-can use resuable inference rules to make more blanket statements such as
+can use reusable inference rules to make more blanket statements such as
 ``Where the title has been set for Facebook's Open Graph, use the same
@@
 
-This may sound too open to problems where properties are miused in
+This may sound too open to problems where properties are misused in
 unexpected ways and that inferring information in key vocabularies from
@@
 decentralisation bring overall maintainability and interoperability benefits
-that outweigh minor integrity concerns that organisations tradtionally attempt
+that outweigh minor integrity concerns that organisations traditionally attempt
 to prevent with strict, controlled vocabularies, governance and bespoke
@@
 correctly used by BBC News and other content producers use it incorrectly. In
-this case, we can update our rules as shown below:
+this case, we can update our rules as shown in listing~\ref{lst:headline-strict}.
+
+Here we add an additional constraint
+that we only infer the \texttt{schema:headline} property that we might
+ultimately use on the search results page from the \texttt{rnews:headline} if
+the content has a value for \texttt{og:site\_name} that indicates it came
+from BBC News. This can then be iterated on for future rules that define
+different behaviour based on different aspects of the content. These inference
+rules can be as simple or as complex as needed.
 
 \begin{centering}
-\begin{lstlisting}[language=ttl]
+\begin{lstlisting}[language=ttl,label=lst:headline-strict,caption=Inference rules where \texttt{rnews:headline} is only used for the headline for content from BBC News.]
 @prefix schema: <http://schema.org/> .
@@
 \end{centering}
-
-Here we add an additional constraint
-that we only infer the \texttt{schema:headline} property that we might
-ultimately use on the search results page from the \texttt{rnews:headline} if
-the content has a value for \texttt{og:site\_name} that indicates it came
-from BBC News. This can then be iterated on for future rules that define
-different behaviour based on different aspects of the content. These inference
-rules can be as simple or as complex as needed.
 
@@
 it can be indexed. Ones that cannot be indexed should be stored, but
-not indexed, so there is opportunity to retrieve and repush items through
+not indexed, so there is opportunity to retrieve and re-push items through
 the Enrichment and Inference stages again if needed.

### 2014-05-20 chapter4.2.tex
Done! Reviewed and ready to submit.

@@
 the results page are out of scope for this proposal, but it is likely
-there could be some improvements in this area, particulary around making
+there could be some improvements in this area, particularly around making
 the web page itself responsive\cite{marcotte2010responsive}. A separate
@@
 the viewpoint of website visitors and consider the relevant
-\emph{search modes} and \emph{mode chains}, which could lead to
+\emph{search modes} and \emph{mode chains}\cite{russell2012designing},
+which could lead to
 an information architecture that would drive metadata requirements.

### 2014-05-20 chapter4.3.tex
Done! Reviewed and ready to submit.

@@
 ``person $X$ is notable for $Y$'' or
-``programme $X$ is a big name brand for the BBC'' and then
+``programme $X$ is a big-name brand for the BBC'' and then
 properties such as \texttt{foaf:homepage}\cite{brickley2012foaf} or

### 2014-05-20 chapter5.1.tex
Done! Reviewed and ready to submit.

@@
 snippets and semi-automated editorial curation are expressed as
-the follow tangible improvments:
+the follow tangible improvements:
 
@@
   In a purely-organic search, it
-  is possible that news articles, etc. might contain the same keywords as a programme (e.g. some programm
+  is possible that news articles, etc. might contain the same keywords as a programme (e.g. some programme
   titles are incredibly generic, such as \emph{Today} on BBC Radio 4) and those results might conceivably

### 2014-05-20 chapter5.2.tex
Done! Reviewed and ready to submit.

@@
 through a process of augmentation, validation and indexing. Recognising
-and exploting Conway's Law\cite{conway1968committees}, a good strategy
+and exploiting Conway's Law\cite{conway1968committees}, a good strategy
 would be to focus subteams on each major area of the application
@@
     generate notifications where such mechanisms do not already exist for certain
-    types of content. Typical considerions will be around RSS/Atom feeds that
+    types of content. Typical considerations will be around RSS/Atom feeds that
     might notify of new content, message-based notifications from other
@@
     will be maintained by a subteam responsible for accepting, validating,
-    archiving, indexing and reindexing content. The Ingest API will have
+    archiving, indexing and re-indexing content. The Ingest API will have
     not just the enrichment stages as a client, but also any BBC team that
@@
     indexes can be reorganised and rebuilt if their structure need to change. It
-    is also possible that the archived content might be repushed via the
+    is also possible that the archived content might be re-pushed via the
     enrichment stages to take advantage of new business rules added therein by
@@
     structure of indexes, configuring linguistic matching and otherwise
-    optmising retrieval that it might prove necessary to split out a subteam
+    optimising retrieval that it might prove necessary to split out a subteam
     dedicated to those tasks.
@@
 The loose coupling afforded by linked data and REST should allow these areas
-to evolve independently without changes causes breakages. For example, the
+to evolve independently without changes causing breakages. For example, the
 discovery component should be able to generate more linked data through finding
@@
 an upstream client sending a new XML or JSON format would cause a service to
-start rejecting the requests unless the service was updated at the same time.
+start rejecting the requests unless the service was updated to understand these
+new requests.
 
-Introducing some devops responsibilities to the individual subteams and
+Introducing some devops\cite{huttermann2012devops}
+responsibilities to the individual subteams and
 making use of cloud technology could even permit each subteam to

### 2014-05-20 chapter5.3.tex
Done! Reviewed and ready to submit.

@@
 below the HTML/CSS/Javascript surface. The web application side follows
-a typical stack comprising Javascript/CSS interface, server-side code/templates
+a typical stack comprising JavaScript/CSS interface, server-side code/templates
 to render the pages and a data layer (the search indexes). However, it has been
@@
 
-This has implicates for planning features, stories, tasks, etc. within
+This has implications for planning features, stories, tasks, etc. within
 an Agile methodology as the first story to display the most basically
@@
   \begin{center}
-    \begin{dot2tex}[dot,pgf,scale=0.42,options=-traw]
+    \begin{tikzpicture}[scale=0.6,transform shape]
+    \begin{dot2tex}[dot,pgf,codeonly]
       \input{basic-ontology.dot}
     \end{dot2tex}
+    \end{tikzpicture}
   \end{center}
@@
 ones, but the linked data model always allows us to publish
-mappings to existing vocabularies. However, small, bespoke
+mappings to existing vocabularies. Small, bespoke
 ontologies are arguably easier to define, control and iterate
@@
 The front end application can continue to search the
-existing search indexes independant of any work being done
+existing search indexes independent of any work being done
 to improve the ingest chain. The importance of developing
@@
 The ``Ingest'' subteam needs to ensure the Ingest API can
-accept content meeting the basic vocabulary outline in
+accept content meeting the basic vocabulary outlined in
 figure~\ref{fig:initial-ontology}, validating ones
-that do not contain the basic fields and evolve the API. If
+that do not contain the basic fields. If
 the results page developers choose to alter the domain
 model based on design iterations and user feedback, then
-these changes can propogate back as requirements for the
+these changes can propagate back as requirements for the
 content ingest.
@@
 Elasticsearch is a standalone search server based on Apache Lucene
-that can store, index and retrieve schemaless JSON structures.
+that can store, index and retrieve schema less JSON structures.
 The indexing chain is to deal with RDF graphs, for which JSON-LD
@@
 
-\begin{lstlisting}[language=Python,label=lst:ingest]
+\begin{lstlisting}[language=Python,label=lst:ingest,caption=Python code to index JSON-LD strings in Elasticsearch.]
 from elasticsearch import Elasticsearch
@@
   body = {'jsonld': json.loads(jsonld_string)}
-  ElasticSearch().index(
-    index='search', body=body, doc_type='item')
+  ElasticSearch().index(index='search', body=body)
 \end{lstlisting}
@@
 objects have changed. There are asynchronous, message-based
-systems in place witin the BBC specifically around
+systems in place within the BBC specifically around
 programmes change notifications and the engineered solution
 is likely to make use of that.
+
+The URLFetch component should be able to create an RDF graph
+like that depicted in figure~\ref{question-time} by
+fetching the microsite for the changed programme object
+and parsing any RDFa and/or Microdata. In listing~\ref{lst:rdfa},
+we can see this is achieved quite succinctly with the
+RDFLib library's built-in support for metadata embedded within
+HTML documents. The function takes any RDF graph (e.g. the minimal
+graph shown in listing~\ref{lst:minimal}), attempts to look up
+all subjects by their URI and adds any RDF metadata found.
+
+\begin{lstlisting}[language=Python,label=lst:rdfa,caption=Use of RDFLib to deference all subjects in upstream graph far and add any linked data found.]
+def fetch_metadata_about_subjects(graph):
+  for subject in graph.subjects():
+    graph.parse(str(subject))
+\end{lstlisting}
 
@@
 to the ontology and vocabulary used in the search application.
-Such rules will extend the form introduced in
-section~\ref{sec:ld-indexing}.
+Such rules will extend the examples introduced in
+section~\ref{sec:ld-indexing}. A simple function that
+uses \emph{RDFLib} and \emph{FuXi} Python libraries to infer
+properties using a given rule set is shown in listing~\ref{lst:infer}.
+
+\begin{lstlisting}[language=Python,label=lst:infer,caption=Python code to expand an RDFLib Graph with inferred properties using FuXi.]
+from rdflib import Graph
+from FuXi.Rete.RuleStore import SetupRuleStore
+from FuXi.Rete.Util import generateTokenSet
+from FuXi.Horn.HornRules import HornFromN3
+
+def apply_inference_rules(graph, ruleset):
+  rule_store, rule_graph, network \
+    = SetupRuleStore(makeNetwork=True)
+  closure_delta = Graph()
+  network.inferredFacts = closure_delta
+  for rule in HornFromN3(ruleset):
+    network.buildNetworkFromClause(rule)
+
+  network.feedFactsToAdd(generateTokenSet(graph))
+
+  return graph + closure_delta
+\end{lstlisting}
 
@@
 soon expire and the search system might be interested in
-reindexing that programme when the nature of its availability
+re-indexing that programme when the nature of its availability
 on BBC iPlayer changes.
@@
 that query an archive of the linked data ingested to look
-for items that may need reingested. They may need to
+for items that may need re-ingested. They may need to
 place requirements on the Ingest team to store an archive
@@
 suitable to act as both a search service and a NoSQL-style
-document store in one). It is then a decision for teh
+document store in one). It is then a decision for the
 engineers as to whether complex SPARQL queries can mine
@@
 out of date or whether to augment the simple ontology
-in figure~\ref{fig:basic-ontology} with the concept of
+in figure~\ref{fig:initial-ontology} with the concept of
 a search result's information \emph{expiring} as shown in
@@
 
-\begin{figure}
+\begin{figure}[t]
   \begin{center}
-    \begin{dot2tex}[dot,pgf,scale=0.41]
+    \begin{tikzpicture}[scale=0.6,transform shape]
+    \begin{dot2tex}[dot,pgf,codeonly]
       \input{expiring-ontology.dot}
     \end{dot2tex}
+    \end{tikzpicture}
   \end{center}
@@
 should no longer appear in the search indexes, but that the
-information should be considered stale and refetching the data
+information should be considered stale and re-fetching the data
 is recommended. This is not too far removed from Google
-recrawling pages based on some assessment of how often the page
+re-crawling pages based on some assessment of how often the page
 should be checked, but here we can use the semantic metadata
@@
 
-\begin{figure}
+\begin{figure}[t]
   \begin{center}
-    \begin{dot2tex}[dot,pgf,scale=0.41]
+    \begin{tikzpicture}[scale=0.6,transform shape]
+    \begin{dot2tex}[dot,pgf,codeonly]
       \input{recommended-ontology.dot}
     \end{dot2tex}
+    \end{tikzpicture}
   \end{center}
@@
 The enrichment components could be extended to fetch additional
-metadata by integrating against backend services that drive
+metadata by integrating against back-end services that drive
 these sites. Investigations will need to be made around this,

### 2014-05-20 chapter6.tex
Done! Reviewed and ready to submit.

@@
 The shift from enterprise integration to linked enterprise data
-seems particulary suitable for the BBC given the legacy of
+seems particularly suitable for the BBC given the legacy of
 distinct data sources that has built up over time. It is hoped that
-the search application can act as a strong example of the advatanges
+the search application can act as a strong example of the advantages
 of publishing enterprise data as linked data and that integration
@@
 
-Future analysis is recommended to address auxillary features such as
+Future analysis is recommended to address auxiliary features such as
 the autocomplete\cite{morville2010search} feature that appears when a user
@@
 
-Further studies, analsys and proposals after implementations of this proposal
+Further studies, analysis and proposals after implementations of this proposal
 are recommended to investigate the benefits of linking more data

### 2014-05-20 paper.tex
Almost finished chapter 4.
Did some reviewing and trrying to fit diagrams in.
Done! Reviewed and ready to submit.

--- 2014-05-04 paper.tex
@@
 \usepackage{url}
+\usepackage{verbatim}
+
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows}
+\usepackage[autosize]{dot2texi}
+
+\usepackage{xcolor}
+
+ \usepackage{listings}
+
+ \lstset{
+         basicstyle=\footnotesize\ttfamily, % Standardschrift
+         %numbers=left,               % Ort der Zeilennummern
+         numberstyle=\tiny,          % Stil der Zeilennummern
+         %stepnumber=2,               % Abstand zwischen den Zeilennummern
+         numbersep=5pt,              % Abstand der Nummern zum Text
+         tabsize=2,                  % Groesse von Tabs
+         extendedchars=true,         %
+         breaklines=true,            % Zeilen werden Umgebrochen
+         keywordstyle=\color{red},
+    		frame=b,         
+ %        keywordstyle=[1]\textbf,    % Stil der Keywords
+ %        keywordstyle=[2]\textbf,    %
+ %        keywordstyle=[3]\textbf,    %
+ %        keywordstyle=[4]\textbf,   \sqrt{\sqrt{}} %
+         stringstyle=\color{blue}\ttfamily, % Farbe der String
+         showspaces=false,           % Leerzeichen anzeigen ?
+         showtabs=false,             % Tabs anzeigen ?
+         xleftmargin=17pt,
+         framexleftmargin=17pt,
+         framexrightmargin=5pt,
+         framexbottommargin=4pt,
+         %backgroundcolor=\color{lightgray},
+         showstringspaces=false      % Leerzeichen in Strings anzeigen ?        
+ }
+  \usepackage{caption}
+\DeclareCaptionFont{white}{\color{white}}
+\DeclareCaptionFormat{listing}{\colorbox[cmyk]{0.43, 0.35, 0.35,0.01}{\parbox{\textwidth}{\hspace{15pt}#1#2#3}}}
+\captionsetup[lstlisting]{format=listing,labelfont=white,textfont=white, singlelinecheck=false, margin=0pt, font={bf,footnotesize}}
+
+\colorlet{punct}{red!60!black}
+\definecolor{background}{HTML}{EEEEEE}
+\definecolor{delim}{RGB}{20,105,176}
+\colorlet{numb}{magenta!60!black}
+
+\lstdefinelanguage{json}{
+    basicstyle=\normalfont\ttfamily\footnotesize,
+    numbersep=8pt,
+    showstringspaces=false,
+    breaklines=true,
+    literate=
+     *{0}{{{\color{numb}0}}}{1}
+      {1}{{{\color{numb}1}}}{1}
+      {2}{{{\color{numb}2}}}{1}
+      {3}{{{\color{numb}3}}}{1}
+      {4}{{{\color{numb}4}}}{1}
+      {5}{{{\color{numb}5}}}{1}
+      {6}{{{\color{numb}6}}}{1}
+      {7}{{{\color{numb}7}}}{1}
+      {8}{{{\color{numb}8}}}{1}
+      {9}{{{\color{numb}9}}}{1}
+      {:}{{{\color{punct}{:}}}}{1}
+      {,}{{{\color{punct}{,}}}}{1}
+      {\{}{{{\color{delim}{\{}}}}{1}
+      {\}}{{{\color{delim}{\}}}}}{1}
+      {[}{{{\color{delim}{[}}}}{1}
+      {]}{{{\color{delim}{]}}}}{1},
+}
+
+% Language Definitions for Turtle
+\definecolor{olivegreen}{rgb}{0.2,0.8,0.5}
+\definecolor{grey}{rgb}{0.5,0.5,0.5}
+\lstdefinelanguage{ttl}{
+    basicstyle=\normalfont\ttfamily\footnotesize,
+    showstringspaces=false,
+sensitive=true,
+morecomment=[l][\color{grey}]{@},
+morecomment=[l][\color{olivegreen}]{\#},
+morestring=[b][\color{blue}]\",
+}
 
@@
 
+%Options: Sonny, Lenny, Glenn, Conny, Rejne, Bjarne, Bjornstrup
+\usepackage[Bjarne]{fncychap}
+
 \begin{document}
